\headline{{\textbf{\Large\sffamily Mark Your Calendars:}}\\
          {\textbf{\large\sffamily Upcoming Events}}}
\label{2025-06-events}

The events listed below refer to club talks, workshops, UK events, and world events registered with the \href{https://www.ukbonsaiassoc.org/events.html}{UK Bonsai Association} as provisional or confirmed, over the next three months.
\begin{itemize}
    \item \textbf{Thursday 12 June 2025 to Sunday 15 June 2025}
    \\
    South Staffs Bonsai Society Display \\
    At Gardeners World Live \\
    National Exhibition Centre \\
    North Avenue, Marston Green, \\
    Birmingham. B40 1NT.
    \begin{itemize}
        \item \textbf{\emph{Dave Barnsley}} \emph{(01216 822200)} \\
        \href{mailto:davidbarnsley@blueyonder.co.uk}{davidbarnsley@blueyonder.co.uk} 
    \end{itemize}

    \item \textbf{Saturday 14 June 2025}
    \\
    Accrington \& District Bonsai Society Display \\
    At Nursery End Garden Centre, \\
    Harrington Street, Clayton Le Moors, \\
    Accrington. BB5 4DF.
    \\
    \emph{Free. 09:30-17:00.hrs.}
    \\
    \href{https://www.accringtonbonsai.co.uk}{www.accringtonbonsai.co.uk}
    \begin{itemize}
        \item \textbf{\emph{Diane Kennedy}} \emph{(07799 567692)} \\
        \href{mailto:dianestardis@icloud.com}{dianestardis@icloud.com} 
    \end{itemize}

    \item \textbf{Saturday 14 June 2025 to Sunday 15 June 2025}
    \\
    Mid-Herts Bonsai Society \\
    Kingsbury Barn, Branch Road, \\
    St Albans, Hertfordshire. AL3 4SE.
    \\
    \emph{Free. 11:00-17:00.hrs}
    \\
    \href{https://www.midhertsbonsaiclub.co.uk}{www.midhertsbonsaiclub.co.uk}
    \begin{itemize}
        \item \textbf{\emph{Geoff Conybeare}} \emph{(07396 732817)} \\
        \href{mailto:info@midhertsbonsaiclub.co.uk}{info@midhertsbonsaiclub.co.uk} 
    \end{itemize}

    \item \textbf{Sunday 15 June 2025}
    \\
    Bristol Bonsai Society Show \\
    Failand Village Hall, Oxhouse Lane, \\
    Failand, Somerset. BS8 3TS.
    \\
    \emph{£6. Under 16s Free.} \\
    \emph{10:00-16:00.hrs}
    \\
    \href{http://www.bristolbonsaisociety.com/}{www.bristolbonsaisociety.com}
    \begin{itemize}
        \item \textbf{\emph{Mark Wood}} \emph{(07964 249279)} \\
        \href{mailto:bbs-site@outlook.com}{bbs-site@outlook.com} 
    \end{itemize}

    \item \textbf{Sunday 15 June 2025}
    \\
    Bedfordshire Bonsai Society Show \\
    Stockwood Park Discovery Centre, \\
    London Road, Luton, \\
    Bedfordshire. LU1 4LX.
    \\
    \emph{Free. 11:00-16:30.hrs}
    \\
    \href{https://www.bedfordshirebonsaisociety.weebly.com}{www.bedfordshirebonsaisociety.weebly.com}
    \begin{itemize}
        \item \textbf{\emph{Richard Gaiger}} \emph{(07745 507318)} \\
        \href{mailto:r.gaiger@ntlworld.com}{r.gaiger@ntlworld.com} 
    \end{itemize}

    \item \textbf{Sunday 15 June 2025}
    \\
    Chiltern Bonsai Society Show \\
    Liston Hall, Chapel Street, Marlow, \\
    Buckinghamshire, SL7 1DD \\
    Supporting Clubs: \\
    Middlesex Bonsai Society \\
    UK Mini Bonsai Group
    \\
    \emph{£2 -16s Free. 10:00-16:00.hrs.}
    \\
    \href{https://www.chilternbonsai.org.uk}{www.chilternbonsai.org.uk}
    \begin{itemize}
        \item \textbf{\emph{Michael Pegg}} \\
        \href{mailto:mikew.pegg@btinternet.com}{mikew.pegg@btinternet.com} 
        \item \textbf{\emph{Adrian Garnett}} \\
        \href{mailto:adrian.garnett@virginmedia.com}{adrian.garnett@virginmedia.com} 
    \end{itemize}

    \item \textbf{Saturday 21 June 2025}
    \\
    Middlesex Bonsai Society Summer Show \\
    South Harrow Methodist Church, \\
    Walton Avenue, South Harrow, \\
    Middlesex. HA2 8QU.
    \\
    \emph{Free. 10:00-13:00.hrs.}
    \\
    \href{https://middlesexbonsaisociety.weebly.com/}{middlesexbonsaisociety.weebly.com}
    \begin{itemize}
        \item \textbf{\emph{Mark Moreland}} \emph{(07850 771201)} \\
        \href{mailto:markmoreland@live.co.uk}{markmoreland@live.co.uk} 
    \end{itemize}

    \item \textbf{Saturday 21 June 2025}
    \\
    Manchester Bonsai Society Annual Show \\
    At Lymm United Reformed Church, \\
    Brookside Road, Lymm, \\
    Cheshire. WA13 0WQ.
    \\
    \emph{Free. 10:00-16:00.hrs}
    \\
    \href{https://www.manchesterbonsaisociety.uk}{www.manchesterbonsaisociety.uk}
    \begin{itemize}
        \item \textbf{\emph{Wayne Crumpton}} \emph{(07742 111142)} \\
        \href{mailto:mbsmembershipsecretary@gmail.com}{mbsmembershipsecretary@gmail.com} 
    \end{itemize}

    \item \textbf{Sunday 22 June 2025}
    \\
    Blackmore Vale Bonsai Group Show \\
    Charlton Remembrance Hall, \\
    Charlton, Shaftsbury, Dorset. SP7 0PL.
    \\
    \emph{£4.00 Under 16s Free.} \\
    \emph{11:00-15:00.hrs}
    \\
    \href{https://www.blackmorevalebonsaigroup.com}{www.blackmorevalebonsaigroup.com}
    \begin{itemize}
        \item \textbf{\emph{Geoff}} \emph{(07837 781744)} \\
        \href{mailto:m5eay.geoff@btinternet.com}{m5eay.geoff@btinternet.com} 
    \end{itemize}

    \item \textbf{Sunday 22 June 2025}
    \\
    Southend Bonsai Society Spring Show \\
    Ashingdon Memorial Hall, \\
    Ashingdon Road, Rochford, \\
    Essex. SS4 3HF.
    \\
    \emph{£4. 10:00-16:00.hrs}
    \begin{itemize}
        \item \textbf{\emph{Paul Schofield}} \emph{(07942 679688)} \\
        \href{mailto:southendbonsaisociety@gmail.com}{southendbonsaisociety@gmail.com} 
    \end{itemize}

    \item \textbf{Sunday 29 June 2025}
    \\
    Twickenham Bonsai Club Summer Show \\
    St Richard Reynolds Catholic College, \\
    Clifden Road, Twickenham. TW1 4LT.
    \\
    \emph{10:00-14:00.hrs £5 Adults} \\
    \emph{14:00-16:00.hrs £2.50 Adults} \\
    \emph{Accompanied under 16.yrs Free.}
    \\
    \href{https://www.twbclub.uk}{www.twbclub.uk}
    \begin{itemize}
        \item \textbf{\emph{Tina Todd}} \emph{(07801 582553)} \\
        \href{mailto:toddytl@hotmail.co.uk}{toddytl@hotmail.co.uk} 
    \end{itemize}

    \item \textbf{Sunday 29 June 2025}
    \\
    Penkridge Bonsai Fair \\
    Penkridge Markets, \\
    Clovelly, Pinfold Lane, \\
    Penkridge, Staffordshire. ST19 5AP.
    \\
    \emph{Free. 09:00-14:00.hrs}
    \begin{itemize}
        \item \textbf{\emph{Mark Akins}} \\
        \href{mailto:penkridge@beechfieldbonsai.co.uk}{penkridge@beechfieldbonsai.co.uk} 
    \end{itemize}

    \item \textbf{Tuesday 1 July 2025 to Sunday 6 July 2025}
    \\
    UKBA Bonsai Display \\
    Hampton Court Palace Garden Festival \\
    East Molesley, Surrey. KT8 9AU.
    \begin{itemize}
        \item \textbf{\emph{Russell Wheeler}} \emph{(07810 372377)} \\
        \href{mailto:russboy23@gmail.com}{russboy23@gmail.com} 
    \end{itemize}

    \item \textbf{Sunday 13 July 2025}
    \\
    Surrey Heath Bonsai Show \\
    Chobham Village Hall, \\
    Station Road, Chobham, \\
    Surrey. GU24 8AQ. \\
    Supporting Club: \\
    UK Mini Bonsai Group
    \\
    \emph{Free. 10:00-16:00.hrs.}
    \\
    \href{https://www.surreyheathbonsai.org.uk}{www.surreyheathbonsai.org.uk}
    \begin{itemize}
        \item \textbf{\emph{Chris Rhodes}} \emph{(01276 20893)} \\
        \href{mailto:rhodes163@googlemail.com}{rhodes163@googlemail.com} 
    \end{itemize}

    \item \textbf{Friday 18 July 2025 to Sunday 20 July 2025}
    \\
    Accrington \& District Bonsai Society Display \\
    At Royal Lancashire Show, \\
    Salesbury Hall, Salesbury Hall Road, \\
    Ribchester, Lancashire. PR3 3XR.
    \\
    \emph{tba. 09:30-17:00.hrs.}
    \\
    \href{https://www.accringtonbonsai.co.uk}{www.accringtonbonsai.co.uk}
    \begin{itemize}
        \item \textbf{\emph{Diane Kennedy}} \emph{(07799 567692)} \\
        \href{mailto:dianestardis@icloud.com}{dianestardis@icloud.com} 
    \end{itemize}

    \item \textbf{Saturday 19 July 2025}
    \\
    Surrey Heath Bonsai Society Display \\
    At Wood Street Village Show, \\
    Village Green, Wood Street, \\
    Guildford, Surrey. GU3 3EU
    \\
    \emph{Free. 12:00-17:00.hrs.}
    \\
    \href{https://www.surreyheathbonsai.org.uk}{www.surreyheathbonsai.org.uk}
    \begin{itemize}
        \item \textbf{\emph{Chris Rhodes}} \emph{(01276 20893)} \\
        \href{mailto:rhodes163@googlemail.com}{rhodes163@googlemail.com} 
    \end{itemize}

    \item \textbf{Saturday 19 July 2025 to Sunday 20 July 2025}
    \\
    Chichester Bonsai Exhibition \\
    Manor Nursery, Pagham Road, \\
    Runcton, Chichester. PO20 1LJ. \\
    Supporting Trader: \\
    Collette's Bonsai
    \\
    \emph{Free. 10:00-16:00 \& 10:00-15:00.hrs.}
    \\
    \href{http://www.chichesterbonsai.uk/}{www.chichesterbonsai.uk}
    \begin{itemize}
        \item \textbf{\emph{Liz Panton}} \emph{(07368 327244)} \\
        \href{mailto:lizpanton5@gmail.com}{lizpanton5@gmail.com} 
    \end{itemize}

    \item \textbf{Sunday 20 July 2025}
    \\
    Akamatsu School Of Bonsai Club Show \\
    Azure Garden Centre, \\
    Station Road, Cramlington, \\
    Northumberland. NE23 8BJ.
    \\
    \emph{Free. 1000-1600.hrs}
    \begin{itemize}
        \item \textbf{\emph{Graham Walker}} \emph{(01287 637734)} \\
        \href{mailto:graham.walker11@ntlworld.com}{graham.walker11@ntlworld.com} 
    \end{itemize}
\end{itemize}
\closearticle
