\headline{{\textbf{\Large\sffamily Mark Your Calendars:}}\\
          {\textbf{\large\sffamily Upcoming Events}}}
\label{2025-09-events}
\noindent
The events listed below refer to club talks, workshops, UK events, and world events registered with the \href{https://www.ukbonsaiassoc.org/events.html}{UK Bonsai Association} as provisional or confirmed, over the next three months.

\begin{itemize}
    \item \textbf{Friday 19 September 2025 to Sunday 21 September 2025}
    \\
    Yorkshire Bonsai Society Display \& Show \\
    At Harrogate Autumn Flower Show, \\
    Newby Hall, Ripon, \\
    North Yorkshire. HG4 5AE.
    \\
    \emph{tba. (Exhibitors Free)} \\
    \emph{10:00-17:00.hrs}
    \begin{itemize}
        \item \textbf{\emph{Craig Brown}} \emph{(07763 771701)} \\
        \href{mailto:jcraig008@sky.com}{jcraig008@sky.com} 
    \end{itemize}

    \item \textbf{Saturday 20 September 2025 to Sunday 21 September 2025}
    \\
    Sutton Bonsai Society Show \\
    Wisley Gardens, Wisley Lane, \\
    Wisley, Surrey. GU23 6QB \\
    Supporting Traders: \\
    Christine \& Stewart Bonsai Pots \\
    Dave Cheshire Bonsai
    \\
    \emph{tba 10:00-16:30}
    \\
    \href{https://www.suttonbonsai.co.uk}{www.suttonbonsai.co.uk}
    \begin{itemize}
        \item \textbf{\emph{Andy Jordan}} \emph{(07958 372101)} \\
        \href{mailto:antique.netsuke@gmail.com}{antique.netsuke@gmail.com} 
    \end{itemize}

    \item \textbf{Sunday 21 September 2025}
    \\
    South East Bonsai Fair \\
    Little Fant Farm, Farleigh Lane, \\
    Maidstone, Kent. ME16 9LY. \\
    Supporting Clubs: \\
    South East Bonsai Society \\
    UK Mini Bonsai Group
    \\
    \emph{Free. 10:00-15:00}
    \begin{itemize}
        \item \textbf{\emph{Adam Hadley}} \emph{(07765 522117)} \\
        \href{mailto:hadoribonsai@gmail.com}{hadoribonsai@gmail.com} 
    \end{itemize}

    \item \textbf{Saturday 27 September 2025}
    \\
    UK Bonsai Association Workshop \\
    with Peter Warren. \\
    Subject: Art Of Displaying. \\
    Chobham Village Hall, \\
    Station Road, Chobham, \\
    Surrey. GU24 8AQ \\
    Workshop 09:45/10:00-17:00.hrs
    \\
    \emph{tba. Pre-bookings only.}
    \begin{itemize}
        \item \textbf{\emph{Steve Hale}} \\
        \href{mailto:ebuk18@gmail.com}{ebuk18@gmail.com} 
    \end{itemize}

    \item \textbf{Sunday 5 October 2025}
    \\
    14th Heathrow Bonsai Show \\
    Bracknell Leisure Centre, \\
    Bagshot Road, Bracknell, \\
    Berkshire, RG12 9SE.
    \\
    \emph{10:00-15:00 £10 Adults} \\
    \emph{15:00-16:00 £5 Adults} \\
    \emph{Accompanied under 16.yrs Free.} \\
    \emph{\textbf{Supporting Clubs:}} \\
    \emph{Bedfordshire Bonsai Society} \\
    \emph{Berkshire Bonsai Society} \\
    \emph{Blackmore Vale Bonsai Group} \\
    \emph{Bristol Bonsai Society} \\
    \emph{British Suiseki Club} \\
    \emph{Bury St Edmunds \& Cambridge BS} \\
    \emph{Cardiff Bonsai Society} \\
    \emph{Celtic Knot Bonsai} \\
    \emph{Chichester Bonsai Society} \\
    \emph{Chiltern Bonsai Society} \\
    \emph{Crawley Bonsai Society} \\
    \emph{Creative Companions} \\
    \emph{Dragon Bonsai Society} \\
    \emph{Eastleigh Bonsai Society} \\
    \emph{Exeter Bonsai Society} \\
    \emph{Glynderi Bonsai Society} \\
    \emph{International Saikei Association} \\
    \emph{Ipswich Bonsai Club} \\
    \emph{Middlesex Bonsai Society} \\
    \emph{Mid-Herts Bonsai Club} \\
    \emph{Newbury Bonsai Society} \\
    \emph{North London Bonsai Group} \\
    \emph{Northamptonshire Bonsai Society} \\
    \emph{Salisbury Bonsai Society} \\
    \emph{Shiten Bonsai Society} \\
    \emph{Solent Bonsai Society} \\
    \emph{Somerset Bonsai Society} \\
    \emph{South East Bonsai Club} \\
    \emph{South Wales Bonsai Collective} \\
    \emph{Southend Bonsai Society} \\
    \emph{Splinter Bonsai Group} \\
    \emph{Staverton Bonsai Group} \\
    \emph{Surrey Heath Bonsai Society} \\
    \emph{Sussex Bonsai Society} \\
    \emph{Sutton Bonsai Society} \\
    \emph{Swindon Bonsai Society} \\
    \emph{The Bonsai Boys} \\
    \emph{Twickenham Bonsai} \\
    \emph{UK Mini Bonsai Group} \\
    \emph{Warminster Bonsai Society} \\
    \emph{\textbf{Supporting Traders:}} \\
    \emph{Beech Field Bonsai} \\
    \emph{Bonsai Brushstrokes} \\
    \emph{Bonsai Pots By Eddie Curtis} \\
    \emph{Bonsai Pots By Ian Jobling} \\
    \emph{Bonsai4Me} \\
    \emph{Bon-Tag} \\
    \emph{Brookfield Plants} \\
    \emph{Chris Thomas Bonsai} \\
    \emph{Christine And Stewart's Bonsai Pots} \\
    \emph{Collette's Bonsai} \\
    \emph{David Cheshire Bonsai} \\
    \emph{Dave Sampson} \\
    \emph{Dei Ceramics} \\
    \emph{Dragonfly Bonsai Pots} \\
    \emph{European Bonsai Pot Collective} \\
    \emph{Everysprout} \\
    \emph{Glynderi Bonsai} \\
    \emph{GoBonsai Air} \\
    \emph{Gordon Duffett} \\
    \emph{Grain Of Time Ceramics} \\
    \emph{Greenwood Bonsai} \\
    \emph{Hadori Bonsai} \\
    \emph{Hereward Trees} \\
    \emph{House Of British Bonsai \& Yamadori} \\
    \emph{LV Bonsai} \\
    \emph{Mark Beverton Furniture} \\
    \emph{Mendip Bonsai} \\
    \emph{Oakfield Bonsai Supplies} \\
    \emph{Oceana} \\
    \emph{Shohin-Bonsai} \\
    \emph{Spectre Ceramics} \\
    \emph{Springwood Ceramics} \\
    \emph{Suteki} \\
    \emph{UK Bonsai Tables} \\
    \emph{Walsall Studio Ceramics} \\
    \emph{Windybank Bonsai} \\
    \emph{Woodandclay} \\
    \emph{Zac's Bonsai} \\
    \emph{Zenwurzel Woodcrafts}
    \\
    \href{http://www.heathrowbonsai.weebly.com/}{www.heathrowbonsai.weebly.com}
    \begin{itemize}
        \item \textbf{\emph{Mark Moreland}} \emph{(07850 771201)} \\
        \href{mailto:ukbonsaiassociation@gmail.com}{ukbonsaiassociation@gmail.com} 
    \end{itemize}

    \item \textbf{Saturday 11 October 2025 to Sunday 12 October 2025}
    \\
    Dragon Bonsai Autumn Show \\
    Open workshop \& Clinic \\
    Masion Aberglasney Gardens, \\
    Llangathen, Carmarthenshire, \\
    Wales. SA32 8QH.
    \\
    \emph{£9.50 -16s.} \\
    \emph{10:00-16:00/10:00-15:00}
    \begin{itemize}
        \item \textbf{\emph{Chris Thomas}} \emph{(07798 798194)} \\
        \href{mailto:chris.thomas1@sky.com}{chris.thomas1@sky.com} 
    \end{itemize}

    \item \textbf{Saturday 25 October 2025 to Sunday 26 October 2025}
    \\
    Greenwood Bonsai Autumn Exhibition \\
    Greenwood Bonsai Studio, \\
    Ollerton Road, Arnold, Nottingham. NG5 8PR.
    \\
    \emph{Free. 10:00-17:00}
    \\
    \href{https://www.bonsai.co.uk}{www.bonsai.co.uk}
    \begin{itemize}
        \item \textbf{\emph{Corin Tomlinson}} \emph{(01159 205757)} \\
        \href{mailto:office@bonsai.co.uk}{office@bonsai.co.uk} 
    \end{itemize}

    \item \textbf{Sunday 26 October 2025}
    \\
    Blackmore Vale Bonsai Group Auction \\
    Charlton Remembrance Hall, \\
    Charlton, Shaftsbury, Dorset. SP7 0PL.
    \\
    \emph{Free. 08:30/11:00-17:00}
    \\
    \href{https://www.blackmorevalebonsaigroup.com}{www.blackmorevalebonsaigroup.com}
    \begin{itemize}
        \item \textbf{\emph{Geoff}} \emph{(07837 781744)} \\
        \href{mailto:m5eay.geoff@btinternet.com}{m5eay.geoff@btinternet.com} 
    \end{itemize}

    \item \textbf{Saturday 7 February 2026 to Sunday 8 February 2026}
    \\
    Irish National Bonsai Exhibition \\
    The People's Museum, \\
    Pery Square, Limerick, \\
    Ireland. V94 HF53.
    \\
    \emph{tba. 10:00-17:00}
    \begin{itemize}
        \item \textbf{\emph{Philip Donnelly}} \emph{(07990 756988)} \\
        \href{mailto:irishbonsaiexhibition@gmail.com}{irishbonsaiexhibition@gmail.com} 
    \end{itemize}

    \item \textbf{Sunday 15 February 2026}
    \\
    Swindon Bonsai Society Winter Image Show \\
    Grange Leisure Centre, Grange Drive, \\
    Stratton St Margaret, Swindon, \\
    Wiltshire. SN3 4JY.
    \\
    \emph{£7 -16.yrs Free. 10:00-16:00}
    \\
    \href{http://www.swindon-bonsai.co.uk/}{www.swindon-bonsai.co.uk}
    \begin{itemize}
        \item \textbf{\emph{Paul Bowerbank}} \emph{(07982 401103)} \\
        \href{mailto:mailto:paul1561@virginmedia.com}{mailto:paul1561@virginmedia.com} 
    \end{itemize}

    \item \textbf{Sunday 8 March 2026}
    \\
    Penkridge Bonsai Fair \\
    Penkridge Markets, \\
    Clovelly, Pinfold Lane, \\
    Penkridge, Staffordshire. ST19 5AP.
    \\
    \emph{Free. 09:00-16:00}
    \begin{itemize}
        \item \textbf{\emph{Mark Akins}} \\
        \href{mailto:penkridge@beechfieldbonsai.co.uk}{penkridge@beechfieldbonsai.co.uk} 
    \end{itemize}

    \item \textbf{Sunday 22 March 2026}
    \\
    South East Bonsai Fair \\
    Little Fant Farm, Farleigh Lane, \\
    Maidstone, Kent. ME16 9LY.
    \\
    \emph{Free. 10:00-15:00}
    \begin{itemize}
        \item \textbf{\emph{Adam Hadley}} \emph{(07765 522117)} \\
        \href{mailto:hadoribonsai@gmail.com}{hadoribonsai@gmail.com} 
    \end{itemize}

    \item \textbf{Sunday 22 March 2026}
    \\
    Bonsai -Fest \\
    George Stephenson Hall, \\
    Newark Showground, \\
    Lincoln Road, Newark, \\
    Nottinghamshire. NG24 2NY.
    \\
    \emph{£12.50. -16s Free. 09:00-16:00}
    \begin{itemize}
        \item \textbf{\emph{Adam Booty}} \\
        \href{mailto:info@bonsai-fest.com}{info@bonsai-fest.com} 
    \end{itemize}

    \item \textbf{Sunday 29 March 2026}
    \\
    UK Mini Bonsai Group Show \\
    \& Workshop. \\
    Chobham Village Hall, \\
    Station Road, Chobham, \\
    Surrey. GU24 8AQ. \\
    Workshop 10:00-14:00 \\
    Pre-Bookings Only £20.08 \\
    Show 14:00-16:00 \\
    07394.597765 (Whatsapp Only) \\
    \textbf{Supporting Traders:} \\
    Dave Sampson \\
    David Cheshire Bonsai \\
    European Bonsai Pot Collective
    \\
    \emph{£3 cash.}
    \\
    \href{https://www.ukminibonsaigroup.weebly.com}{www.ukminibonsaigroup.weebly.com}
    \begin{itemize}
        \item \textbf{\emph{Gary}} \\
        \href{mailto:ukminibonsaigroup@gmail.com}{ukminibonsaigroup@gmail.com} 
    \end{itemize}

    \item \textbf{Sunday 29 March 2026}
    \\
    UK Bonsai Association Workshop \\
    with various speakers \\
    Subject: Mini Bonsai \\
    Chobham Village Hall, \\
    Station Road, Chobham, \\
    Surrey. GU24 8AQ. \\
    Workshop 09:45/10:00-13:30.hrs
    \\
    \emph{£20.08 Pre-bookings only.}
    \begin{itemize}
        \item \textbf{\emph{Mark Moreland}} \emph{(07850 771201)} \\
        \href{mailto:ukbonsaiassociation@gmail.com}{ukbonsaiassociation@gmail.com} 
    \end{itemize}

    \item \textbf{Sunday 12 April 2026}
    \\
    7th Expo Bonsai UK \\
    Sponsored by UKBA \\
    K2 Leisure Centre, \\
    Pease Pottage Hill, Crawley, \\
    West Sussex. RH11 9BQ
    \\
    \emph{10:00-14:00 £10 Adults} \\
    \emph{15:00-16:00 £5 Adults} \\
    \emph{- 16s Free.}
    \\
    \href{http://www.expobonsaiuk.weebly.co/}{www.expobonsaiuk.weebly.co}
    \begin{itemize}
        \item \textbf{\emph{Steve Hale}} \emph{(07850 771201)} \\
        \href{mailto:ebuk18@gmail.com}{ebuk18@gmail.com} 
    \end{itemize}

    \item \textbf{Thursday 23 April 2026 to Sunday 26 April 2026}
    \\
    Yorkshire Bonsai Society Display \& Show \\
    At Harrogate Spring Flower Show, \\
    Great Yorkshire Showground, \\
    Railway Road, Harrogate, \\
    North Yorkshire. HG2 8NZ.
    \\
    \emph{tba. (Exhibitors Free).} \\
    \emph{10:00-17:00}
    \begin{itemize}
        \item \textbf{\emph{Craig Brown}} \emph{(07763 771701)} \\
        \href{mailto:jcraig008@sky.com}{jcraig008@sky.com} 
    \end{itemize}

    \item \textbf{Saturday 9 May 2026}
    \\
    World Bonsai Day

    \item \textbf{Sunday 10 May 2026}
    \\
    Ayrshire Bonsai Club Open Exhibition \\
    Troon Concert Hall, \\
    South Beach, Troon. \\
    Ayrshire. KA10 6EF.
    \\
    \emph{£2.50. 11:00-16:00}
    \begin{itemize}
        \item \textbf{\emph{Jeff Banning}} \emph{(07799 477895)} \\
        \href{mailto:jeffbanning@btinternet.com}{jeffbanning@btinternet.com} 
    \end{itemize}

    \item \textbf{Saturday 16 May 2026 to Sunday 17 May 2026}
    \\
    Greenwood Spring Bonsai Bash \\
    Greenwood Bonsai Studio, \\
    Ollerton Road, Arnold, Nottingham. NG5 8PR.
    \\
    \emph{Free. 10:00-17:00}
    \\
    \href{https://www.bonsai.co.uk}{www.bonsai.co.uk}
    \begin{itemize}
        \item \textbf{\emph{Corin Tomlinson}} \emph{(01159 205757)} \\
        \href{mailto:office@bonsai.co.uk}{office@bonsai.co.uk} 
    \end{itemize}

    \item \textbf{Sunday 17 May 2026}
    \\
    Chiltern Bonsai Society Show \\
    Liston Hall, Chapel Street, Marlow, \\
    Buckinghamshire, SL7 1DD \\
    Supporting Clubs: \\
    Middlesex Bonsai Society \\
    UK Mini Bonsai Group
    \\
    \emph{£3 -16s Free. 10:00-15:00}
    \\
    \href{https://www.chilternbonsai.org.uk}{www.chilternbonsai.org.uk}
    \begin{itemize}
        \item \textbf{\emph{Michael Pegg}} \\
        \href{mailto:mikew.pegg@btinternet.com}{mikew.pegg@btinternet.com} 
        \item \textbf{\emph{Adrian Garnett}} \\
        \href{mailto:adrian.garnett@virginmedia.com}{adrian.garnett@virginmedia.com} 
    \end{itemize}

    \item \textbf{Saturday 23 May 2026}
    \\
    North London Bonsai Group Show \\
    Capel Manor, Bullsmoor Lane, \\
    Enfield, Middlesex. EN1 4RQ. \\
    Supporting Club: \\
    UK Mini Bonsai Group
    \\
    \emph{tba. 10:00-16:00}
    \begin{itemize}
        \item \textbf{\emph{Bob McGregor}} \emph{(07903 710509)} \\
        \href{mailto:dismcg@hotmail.co.uk}{dismcg@hotmail.co.uk} 
    \end{itemize}

    \item \textbf{Sunday 31 May 2026}
    \\
    UK Bonsai Association Auction \\
    Chobham Village Hall, \\
    Station Road, Chobham, \\
    Surrey. GU24 8AQ. \\
    The auction is strictly cash only please. \\
    Please visit the auction website for further details \\
    Submissions pre-booked or on the morning.
    \\
    \emph{£3 cash. -16s FREE. 1100-1600}
    \\
    \href{https://www.ukbonsaiauction.weebly.com}{www.ukbonsaiauction.weebly.com}
    \begin{itemize}
        \item \textbf{\emph{Chris Thomas}} \emph{(07798 798194)} \\
        \href{mailto:chris.thomas1@gmail.com}{chris.thomas1@gmail.com} 
        \item \textbf{\emph{Mark Moreland}} \emph{(07850 771201)} \\
        \href{mailto:markmoreland@live.co.uk}{markmoreland@live.co.uk} 
    \end{itemize}

    \item \textbf{Thursday 11 June 2026 to Sunday 14 June 2026}
    \\
    South Staffs Bonsai Society Display \\
    At Gardeners World Live \\
    National Exhibition Centre \\
    North Avenue, Marston Green, \\
    Birmingham. B40 1NT.
    \begin{itemize}
        \item \textbf{\emph{Dave Barnsley}} \emph{(01216 822200)} \\
        \href{mailto:davidbarnsley@blueyonder.co.uk}{davidbarnsley@blueyonder.co.uk} 
    \end{itemize}

    \item \textbf{Sunday 21 June 2026}
    \\
    Blackmore Vale Bonsai Group Show \\
    Charlton Remembrance Hall, \\
    Charlton, Shaftsbury, Dorset. SP7 0PL. \\
    Refreshments Free \\
    \textbf{Demonstrations:} \\
    Tony Oswin \\
    Bob Burkin \\
    \textbf{Supporting Clubs:} \\
    Somerset Bonsai Society \\
    Staverton Bonsai Group \\
    UK Mini Bonsai Group \\
    Warminster Bonsai Society \\
    \textbf{Supporting Traders:} \\
    Chris Thomas Bonsai \\
    Oakfield Bonsai Supplies
    \\
    \emph{£4.00 -16s Free. 11:00-15:00}
    \\
    \href{https://www.blackmorevalebonsaigroup.com}{www.blackmorevalebonsaigroup.com}
    \begin{itemize}
        \item \textbf{\emph{Geoff}} \emph{(07837 781744)} \\
        \href{mailto:m5eay.geoff@btinternet.com}{m5eay.geoff@btinternet.com} 
    \end{itemize}

    \item \textbf{Friday 18 September 2026 to Monday 21 September 2026}
    \\
    Yorkshire Bonsai Society Display \& Show \\
    At Harrogate Autumn Flower Show, \\
    Newby Hall, Ripon, \\
    North Yorkshire. HG4 5AE.
    \\
    \emph{tba. (Exhibitors Free)} \\
    \emph{10:00-17:00.hrs}
    \begin{itemize}
        \item \textbf{\emph{Craig Brown}} \emph{(07763 771701)} \\
        \href{mailto:jcraig008@sky.com}{jcraig008@sky.com} 
    \end{itemize}

    \item \textbf{Sunday 20 September 2026}
    \\
    South East Bonsai Fair \\
    Little Fant Farm, Farleigh Lane, \\
    Maidstone, Kent. ME16 9LY.
    \\
    \emph{Free. 10:00-15:00}
    \begin{itemize}
        \item \textbf{\emph{Adam Hadley}} \emph{(07765 522117)} \\
        \href{mailto:hadoribonsai@gmail.com}{hadoribonsai@gmail.com} 
    \end{itemize}

    \item \textbf{Sunday 4 October 2026}
    \\
    15th Heathrow Bonsai Show \\
    Bracknell Leisure Centre, \\
    Bagshot Road, Bracknell, \\
    Berkshire, RG12 9SE.
    \\
    \emph{10:00-15:00 £10 Adults} \\
    \emph{15:00-16:00 £5 Adults} \\
    \emph{Accompanied under 16.yrs Free.}
    \\
    \href{http://www.heathrowbonsai.weebly.com/}{www.heathrowbonsai.weebly.com}
    \begin{itemize}
        \item \textbf{\emph{Mark Moreland}} \emph{(07850 771201)} \\
        \href{mailto:ukbonsaiassociation@gmail.com}{ukbonsaiassociation@gmail.com} 
    \end{itemize}

\end{itemize}
\closearticle