\headline{{\textbf{\Large\sffamily Mark Your Calendars:}}\\
          {\textbf{\large\sffamily Upcoming Events}}}
\label{2025-08-events}
\noindent
The events listed below refer to club talks, workshops, UK events, and world events registered with the \href{https://www.ukbonsaiassoc.org/events.html}{UK Bonsai Association} as provisional or confirmed, over the next three months.

\begin{itemize}
    \item \textbf{Saturday 30 August 2025}
    \\
    UK Mini Bonsai Group Show \\
    \& UKBA Workshop. \\
    David Cheshire Nurseries Ltd \\
    Mill Hill, Baginton, \\
    Coventry, Warwickshire. CV8 3AG. \\
    Workshop 10:00-14:00 \\
    Pre-Bookings Only £20.06 \\
    Show 14:00-16:00.hrs \\
    07394.597765 (Whatsapp Only) \\
    <u>Supporting Traders:</u> \\
    David Cheshire Bonsai \\
    David Harris \\
    David Sampson \\
    European Bonsai Potters Collective \\
    Grain Of Time \\
    Shohin Bonsai
    \\
    \emph{£3 cash.}
    \\
    \href{https://www.ukminibonsaigroup.weebly.com}{www.ukminibonsaigroup.weebly.com}
    \begin{itemize}
        \item \textbf{\emph{Gary Careford}} \\
        \href{mailto:ukminibonsaigroup@gmail.com}{ukminibonsaigroup@gmail.com} 
    \end{itemize}

    % \item \textbf{Saturday 30 August 2025}
    % \\
    % UK Bonsai Association Workshop \\
    % with various speakers \\
    % Subject: Mini Bonsai \\
    % David Cheshire Nurseries Ltd \\
    % Mill Hill, Baginton, \\
    % Coventry, Warwickshire. CV8 3AG. \\
    % Workshop 09:45/10:00-14:00.hrs \\
    % Alex Rudd - \\
    % Bonsai pots for Mame \\
    % David Cheshire - \\
    % Japanese growing techniques for Mame \\
    % John Armitage - \\
    % Bonsai Display \\
    % Mark Moreland - \\
    % Humidity in Bonsai
    % \\
    % \emph{£20.06 Pre-bookings only.}
    % \begin{itemize}
    %     \item \textbf{\emph{Mark Moreland}} \emph{(07850 771201)} \\
    %     \href{mailto:ukbonsaiassociation@gmail.com}{ukbonsaiassociation@gmail.com} 
    % \end{itemize}

    \item \textbf{Sunday 31 August 2025}
    \\
    Bonsai Shed Car Booty \\
    Wood Stock Lane North, \\
    Hill Park Rose Centre, \\
    Thames Ditton, Surrey. KT6 5HN.
    \\
    \emph{Free. 09:00-12:00}
    \begin{itemize}
        \item \textbf{\emph{Andrew Barber}} \emph{(07590 595538)} \\
        \href{mailto:foodsmithltd@gmail.com}{foodsmithltd@gmail.com} 
    \end{itemize}

    \item \textbf{Saturday 6 September 2025}
    \\
    Accrington \& District Bonsai Society Display \\
    At Baxenden Alloment \& Garden Show, \\
    The Hollins Technology College, \\
    171 Hollins Lane, Baxenden, \\
    Accrington. BB5 2QY.
    \\
    \emph{Donation. 14:45-17:00}
    \\
    \href{https://www.accringtonbonsai.co.uk}{www.accringtonbonsai.co.uk}
    \begin{itemize}
        \item \textbf{\emph{Diane Kennedy}} \emph{(07799 567692)} \\
        \href{mailto:dianestardis@icloud.com}{dianestardis@icloud.com} 
    \end{itemize}

    \item \textbf{Saturday 6 September 2025 to Sunday 7 September 2025}
    \\
    Dragon Bonsai Workshop \& Auction \\
    Cwmaman Resource Centre, \\
    Station Road, Glanamman, \\
    Wales. SA18 1QL. \\
    Sat Workshop \& BBQ 10:00-Late \\
    Sat night Bunkhouse \& Breakfast £25 \\
    Sun Auction 11:00-14:00
    \\
    \emph{Free.}
    \begin{itemize}
        \item \textbf{\emph{Chris Thomas}} \emph{(07798 798194)} \\
        \href{mailto:chris.thomas1@sky.com}{chris.thomas1@sky.com} 
    \end{itemize}

    \item \textbf{Sunday 7 September 2025}
    \\
    East Anglian Bonsai Show \\
    Kesgrave War Memorial Community Centre, \\
    Twelve Acre Approach, Kesgrave, \\
    Suffolk. IP5 1JF. \\
    Demonstrating: \\
    Will Baddeley \\
    Supporting Clubs: \\
    Bury St Edmunds \& Cambridge B.S \\
    Ipswich Bonsai Society \\
    Middlesex Bonsai Society \\
    Mid-Herts Bonsai Society \\
    Norfolk Bonsai Association \\
    North London Bonsai Group \\
    Southend Bonsai Society \\
    UK Mini Bonsai Group \\
    Supporting Traders: \\
    Bon-Tag \\
    Die Ceramics \\
    EVERY SPROUT \\
    Grain of Time Bonsai \\
    Reid Bonsai \\
    Walsall Ceramics \\
    Wilderness Bonsai \\
    Plus 10 Private sellers
    \\
    \emph{£4.-16.yrs Free. 10:00-15:30}
    \begin{itemize}
        \item \textbf{\emph{Dave Fryer}} \emph{(07749 801297)} \\
        \href{mailto:daveafryer@aol.com}{daveafryer@aol.com} 
    \end{itemize}

    \item \textbf{Saturday 13 September 2025}
    \\
    Berkshire Bonsai Society Display \\
    At Henley Farm \& Country Show \\
    Henley Showground, Marlow road, \\
    Henley-On-Thames. RG9 3AS.
    \\
    \emph{tba. 09:00-18:00}
    \\
    \href{http://www.berkshirebonsai.co.uk/}{www.berkshirebonsai.co.uk}
    \begin{itemize}
        \item \textbf{\emph{Jamie Ewing}} \emph{(07570 368175)} \\
        \href{mailto:jamie1322@hotmail.co.uk}{jamie1322@hotmail.co.uk} 
    \end{itemize}

    \item \textbf{Sunday 14 September 2025}
    \\
    South Staffs Bonsai Society Show \\
    Birmingham Botanical Gardens, \\
    Westbourne Road, Edgbaston, \\
    Birmingham. B15 3TR. \\
    Supporting Trader: \\
    Funky Fish Ceramics \\
    David Cheshire Bonsai
    \\
    \emph{tba. 1000-1700}
    \begin{itemize}
        \item \textbf{\emph{Dave Barnsley}} \emph{(01216 822200)} \\
        \href{mailto:davidbarnsley@blueyonder.co.uk}{davidbarnsley@blueyonder.co.uk} 
    \end{itemize}

    \item \textbf{Saturday 20 September 2025 to Sunday 21 September 2025}
    \\
    Sutton Bonsai Society Show \\
    Wisley Gardens, Wisley Lane, \\
    Wisley, Surrey. GU23 6QB
    \\
    \emph{tba 10:00-16:30}
    \\
    \href{https://www.suttonbonsai.co.uk}{www.suttonbonsai.co.uk}
    \begin{itemize}
        \item \textbf{\emph{Andy Jordan}} \emph{(07958 372101)} \\
        \href{mailto:antique.netsuke@gmail.com}{antique.netsuke@gmail.com} 
    \end{itemize}

    \item \textbf{Sunday 21 September 2025}
    \\
    South East Bonsai Fair \\
    Little Fant Farm, Farleigh Lane, \\
    Maidstone, Kent. ME16 9LY. \\
    Supporting Club: \\
    UK Mini Bonsai Group
    \\
    \emph{Free. 10:00-15:00}
    \begin{itemize}
        \item \textbf{\emph{Adam Hadley}} \emph{(07765 522117)} \\
        \href{mailto:hadoribonsai@gmail.com}{hadoribonsai@gmail.com} 
    \end{itemize}

    \item \textbf{Saturday 27 September 2025}
    \\
    UK Bonsai Association Workshop \\
    with Peter Warren. \\
    Subject: Art Of Displaying. \\
    Chobham Village Hall, \\
    Station Road, Chobham, \\
    Surrey. GU24 8AQ \\
    Workshop 09:45/10:00-17:00.hrs
    \\
    \emph{tba. Pre-bookings only.}
    \begin{itemize}
        \item \textbf{\emph{Steve Hale}} \\
        \href{mailto:ebuk18@gmail.com}{ebuk18@gmail.com} 
    \end{itemize}

    \item \textbf{Sunday 5 October 2025}
    \\
    14th Heathrow Bonsai Show \\
    Bracknell Leisure Centre, \\
    Bagshot Road, Bracknell, \\
    Berkshire, RG12 9SE.
    \\
    \emph{10:00-15:00 £10 Adults} \\
    \emph{15:00-16:00 £5 Adults} \\
    \emph{Accompanied under 16.yrs Free.} \\
    \emph{Supporting Club:} \\
    \emph{UK Mini Bonsai Group}
    \\
    \href{http://www.heathrowbonsai.weebly.com/}{www.heathrowbonsai.weebly.com}
    \begin{itemize}
        \item \textbf{\emph{Mark Moreland}} \emph{(07850 771201)} \\
        \href{mailto:ukbonsaiassociation@gmail.com}{ukbonsaiassociation@gmail.com} 
    \end{itemize}

    \item \textbf{Saturday 11 October 2025 to Sunday 12 October 2025}
    \\
    Dragon Bonsai Autumn Show \\
    Open workshop \& Clinic \\
    Masion Aberglasney Gardens, \\
    Llangathen, Carmarthenshire, \\
    Wales. SA32 8QH.
    \\
    \emph{£9.50 -16s.} \\
    \emph{10:00-16:00/10:00-15:00}
    \begin{itemize}
        \item \textbf{\emph{Chris Thomas}} \emph{(07798 798194)} \\
        \href{mailto:chris.thomas1@sky.com}{chris.thomas1@sky.com} 
    \end{itemize}

    \item \textbf{Saturday 25 October 2025 to Sunday 26 October 2025}
    \\
    Greenwood Bonsai Autumn Exhibition \\
    Greenwood Bonsai Studio, \\
    Ollerton Road, Arnold, Nottingham. NG5 8PR.
    \\
    \emph{Free. 10:00-17:00}
    \\
    \href{https://www.bonsai.co.uk}{www.bonsai.co.uk}
    \begin{itemize}
        \item \textbf{\emph{Corin Tomlinson}} \emph{(01159 205757)} \\
        \href{mailto:office@bonsai.co.uk}{office@bonsai.co.uk} 
    \end{itemize}

    \item \textbf{Sunday 26 October 2025}
    \\
    Blackmore Vale Bonsai Group Auction \\
    Charlton Remembrance Hall, \\
    Charlton, Shaftsbury, Dorset. SP7 0PL.
    \\
    \emph{Free. 08:30/11:00-17:00}
    \\
    \href{https://www.blackmorevalebonsaigroup.com}{www.blackmorevalebonsaigroup.com}
    \begin{itemize}
        \item \textbf{\emph{Geoff}} \emph{(07837 781744)} \\
        \href{mailto:m5eay.geoff@btinternet.com}{m5eay.geoff@btinternet.com} 
    \end{itemize}

\end{itemize}
\closearticle