\headline{{\textbf{\Large\sffamily The Top Chop:}}\\
          {\textbf{\large\sffamily The Tree of the Month Contest}}}
\label{2025-08-contest}
\noindent
The August meeting of Twickenham Bonsai Club was a display of gravity\--defying elegance, as members embraced the flowing theme: \textit{``Cascade or Semi\--Cascade''}.
From sweeping, dramatic falls of foliage to more subtle, leaning forms, each tree embodied movement and grace.
The benches were a spectacular sight, evoking trees clinging to mountain slopes and cascading down riverbanks.

\topic{Tree of the Month}
\noindent 
This month's display was a masterclass in dynamic composition and vertical drama.

\begin{enumerate}
    \item \textbf{Terry Wilson}'s Juniper (\textit{`Juniperus'}, 150 points).
    \item \textbf{Tina Todd}'s Cotoneaster (\textit{`Cotoneaster'}, 144 points).
    \item \textbf{David Fishwick}'s Cotoneaster (\textit{`Cotoneaster'}, 140 points).
    \item \textbf{Paul Owen}'s Scots Pine (\textit{`Pinus Sylvestris'}, 133 points).
    \item \textbf{Nick Lloyd}'s Sabina Juniper (\textit{`Juniperus Sabina'}, 127 points).
    \item \textbf{Chris Durne}'s Cotoneaster (\textit{`Cotoneaster'}, 116 points).
    \item \textbf{Mark Angold}'s Juniper (\textit{`Juniperus'}, 117 points).
    \item \textbf{Haidi Jenkin}'s Scots Pine (\textit{`Pinus Sylvestris'}, 105 points).
    \item \textbf{Grant Kinnaird}'s Cotoneaster (\textit{`Cotoneaster'}, 88 points).
    \item \textbf{Brendan Gibbs}' Cotoneaster (\textit{`Cotoneaster'}, 31 points).
    \item \textbf{Graham Stevenson}'s Oak (\textit{`Quercus'}, 74 points).
    \item \textbf{Victoria Miquel}'s Apple tree (\textit{`Malus'}, 68 points).
\end{enumerate}

\noindent 
\textbf{Terry Wilson} claims this month's top prize with his magnificent cascading \textit{Juniper} --- a stunning example of the style executed to perfection!

\topic{Novice Tree of the Month}
\noindent
Our novice category embraced the challenge of the cascade with impressive results.

\begin{enumerate}
    \item \textbf{John Mani}'s Pine (\textit{`Pinus'}, 39 points).
\end{enumerate}

\noindent
\textbf{John Mani} takes this month’s novice honour with his well\--presented Pine --- well done!

\vspace{-0.25em}
\begin{center}
    $\cdots$
\end{center}
\vspace{-0.25em}

\noindent
This month’s entries proved the captivating beauty of the cascade and semi\--cascade styles --- each tree a frozen moment of flow and elegance.
Looking ahead, September’s theme invites enduring beauty with \textit{``Evergreen''}.
Until then --- keep your trees flowing and your spirits high!
\closearticle
\columnbreak
