\headline{{\textbf{\Large\sffamily Planning Workshops 2026:}}\\
          {\textbf{\large\sffamily We Listen To You!}}}
\noindent
Following recent discussions, the TWBC Committee is pleased to share the proposed plans for member activities in the coming year.
We are excited to announce the launch of a new \textbf{Member Education Programme (MEP)}, designed to provide more hands\--on learning opportunities.
% The response from the membership has been very encouraging, with 19 members already voting in favour of the initiative.

The programme will begin with two Saturday morning workshops heald at the Whitton Community Centre.
The first is scheduled for \textbf{Saturday, 13th December}, and will focus on \textbf{winter structural pruning and wiring}.
The second is set for \textbf{Saturday, 17th January}, and will be about \textbf{repotting}.

Each workshop is limited to six participants.
Three spots for both dates are already taken, so please contact Tony Ulatowski promptly to reserve your place.
The club will cover hall hire, and participants may offer the instructor a voluntary red envelope (lai see) as a token of thanks, following tradition.

In addition, the committee has also been busy confirming a lineup of guest artists for 2026.
We are delighted to have secured the following experts:

\begin{itemize}
    \item \textbf{John Hanby} (\url{https://www.johnhanbybonsai.co.uk/}, \textit{March 2026}), a true pioneer of British bonsai, will join us for an afternoon workshop and an evening club talk.

    \item \textbf{Morten Albek} (\url{https://shohin-europe.com}, \textit{9th-10th May 2026}), an internationally renowned artist and World Bonsai University instructor, will lead a session.

    \item \textbf{Caz Scott} (\url{https://cazbonsai.co.uk/}, \textit{September 2026}), one of the world's leading female bonsai artists, is booked for a club talk and a weekend workshop.
\end{itemize}

These sessions are great opportunities to learn from top\--tier talent.
Spaces will be limited.
For more detailed information, including the specific costs for each guest artist workshop, please check the updates on our Discord server.

\medskip
\noindent
In other news, here are some key reminders for upcoming club activities:

\begin{itemize}
    \item \textbf{Bonsai ``Booty'' Fair - Sun, 31st Aug} \\
    The Bonsai Shed, Thames Ditton.
    A great chance to buy, sell, or trade trees from 9am.
    Perfect for finding a new project.

    \item \textbf{RHS Wisley Visit - Sat, 20th Sep} \\
    Meet at \textbf{10am sharp} at the main car park for our free group entry.
    This trip coincides with the Sutton Bonsai Show.
    Please confirm your ticket numbers.

    \item \textbf{Heathrow Show Display - Sun, 5th Oct} \\
    We are selecting trees for our club display.
    Please submit trees under 60cm for consideration.
    Now is the time to prepare your potential entries.
\end{itemize}
\closearticle
\clearpage
