\headline{{\textbf{\Large\sffamily Mark Your Calendars:}}\\
          {\textbf{\large\sffamily Upcoming Events}}}
\label{2025-11-events}

The events listed below refer to club talks, workshops, UK events, and world events registered with the \href{https://www.ukbonsaiassoc.org/events.html}{UK Bonsai Association} as provisional or confirmed, over the next three months.
\begin{itemize}

    \item \textbf{Sunday 11 January 2026}
    \\
    Ayrshire Bonsai Club Winter Image Show \\
    Alloway Village Hall, 36a Alloway, \\
    Ayrshire. KA7 4PY.
    \\
    \emph{Free. 13:30-17:00}
    \begin{itemize}
        \item \textbf{\emph{Jeff Banning}} \emph{(07799 477895)} \\
        \href{mailto:jeffbanning@btinternet.com}{jeffbanning@btinternet.com}
    \end{itemize}

    \item \textbf{Saturday 17 January 2026}
    \\
    Middlesex Bonsai Society Winter Show \\
    South Harrow Methodist Church, \\
    Walton Avenue, South Harrow, \\
    Middlesex. HA2 8QU.
    \\
    \emph{Free. 10:00-13:00}
    \\
    \href{https://middlesexbonsaisociety.weebly.com/}{middlesexbonsaisociety.weebly.com}
    \begin{itemize}
        \item \textbf{\emph{Mark Moreland}} \emph{(07850 771201)} \\
        \href{mailto:markmoreland@live.co.uk}{markmoreland@live.co.uk}
    \end{itemize}

    \item \textbf{Sunday 1 February 2026}
    \\
    Twickenham Bonsai Club Winter Show \\
    St Richard Reynolds Catholic College, \\
    Clifden Road, Twickenham. TW1 4LT.
    \\
    \emph{10:00-14:00 £5 Adults} \\
    \emph{14:00-16:00 £2.50 Adults} \\
    \emph{Accompanied under 16.yrs Free.}
    \\
    \href{https://www.twbclub.uk}{www.twbclub.uk}
    \begin{itemize}
        \item \textbf{\emph{Tina Todd}} \emph{(07801 582553)} \\
        \href{mailto:toddytl@hotmail.co.uk}{toddytl@hotmail.co.uk}
    \end{itemize}

    \item \textbf{Saturday 7 February 2026 to Sunday 8 February 2026}
    \\
    Irish National Bonsai Exhibition \\
    The People's Museum, \\
    Pery Square, Limerick, \\
    Ireland. V94 HF53.
    \\
    \emph{tba. 10:00-17:00}
    \begin{itemize}
        \item \textbf{\emph{Philip Donnelly}} \emph{(07990 756988)} \\
        \href{mailto:irishbonsaiexhibition@gmail.com}{irishbonsaiexhibition@gmail.com}
    \end{itemize}

    \item \textbf{Sunday 15 February 2026}
    \\
    Swindon Bonsai Society Winter Image Show \\
    Grange Leisure Centre, Grange Drive, \\
    Stratton St Margaret, Swindon, \\
    Wiltshire. SN3 4JY.
    \\
    \emph{£7 -16.yrs Free. 10:00-16:00}
    \\
    \href{http://www.swindon-bonsai.co.uk/}{www.swindon-bonsai.co.uk}
    \begin{itemize}
        \item \textbf{\emph{Paul Bowerbank}} \emph{(07982 401103)} \\
        \href{mailto:mailto:paul1561@virginmedia.com}{mailto:paul1561@virginmedia.com}
    \end{itemize}

\end{itemize}
\closearticle