%!TEX root = /Users/stefano/Documents/Bonsai Club/TWBC/twbc.tex

\headline{{\textbf{\Large\sffamily Mark Your Calendars:}}\\
          {\textbf{\large\sffamily Upcoming Events}}}
\label{2025-01-events}
\noindent
The events listed below refer to club talks, workshops, UK events, and world events registered with the \href{https://www.ukbonsaiassoc.org/events.html}{UK Bonsai Association} as provisional or confirmed, over the next three months.
\begin{itemize}
    \item \textbf{Saturday 18 January 2025}
    \\
    Middlesex Bonsai Society Winter Show \\
    South Harrow Methodist Church, \\
    Walton Avenue, South Harrow, \\
    Middlesex. HA2 8QU.
    \\
    \emph{Free. 10:00-13:00.hrs.}
    \\
    \href{https://middlesexbonsaisociety.weebly.com/}{middlesexbonsaisociety.weebly.com}
    \begin{itemize}
        \item \textbf{\emph{Mark Moreland}} \emph{(07850 771201)} \\
        \href{mailto:markmoreland@live.co.uk}{markmoreland@live.co.uk} 
    \end{itemize}

    \item \textbf{Sunday 2 February 2025}
    \\
    Twickenham Bonsai Club Winter Show \\
    St Richard Reynolds Catholic College, \\
    Clifden Road, Twickenham. TW1 4LT.
    \\
    \emph{10:00-14:00.hrs £5 Adults} \\
    \emph{14:00-16:00.hrs £2.50 Adults} \\
    \emph{Accompanied under 16.yrs Free.}
    \\
    \href{https://www.twbclub.uk}{www.twbclub.uk}
    \begin{itemize}
        \item \textbf{\emph{Tina Todd}} \emph{(07801 582553)} \\
        \href{mailto:toddytl@hotmail.co.uk}{toddytl@hotmail.co.uk} 
    \end{itemize}

    \item \textbf{Sunday 16 February 2025}
    \\
    Swindon Bonsai Society Winter Image Show \\
    Grange Leisure Centre, Grange Drive, \\
    Stratton St Margaret, Swindon, \\
    Wiltshire. SN3 4JY. \\
    Cafe refreshments card payment only. \\
    Please visit Swindon website for further details \\
    Afternoon Talk: \\
    Alex Rudd of European Bonsai Potters Collective \\
    Supporting Clubs: \\
    Aka Matsu School Of Bonsai \\
    Ashfield Bonsai Society \\
    Glynderi Bonsai Society \\
    Newbury Bonsai Society \\
    Solent Bonsai Society \\
    Splinter Group \\
    Surrey Heath Bonsai Society \\
    Twickenham Bonsai Society \\
    Warminster Bonsai Society \\
    Traders: \\
    BW Bespoke Stands \\
    Chris Thomas Bonsai \\
    Christine Beresford Ceramics \\
    Dan Barton Ceramics \\
    Devon Bonsai \\
    Gordon Duffett Pots \\
    Greenwood Bonsai \\
    LV Bonsai \\
    Mendip Bonsai \\
    Suteki \\
    Tony Remington Ceramics \\
    Walsall Studio Ceramics \\
    Windybank Bonsai \\
    Wood \& Clay Ceramics \\
    Zac's Bonsai
    \\
    \emph{£7. Accompanied under 16.yrs Free.} \\
    \emph{10:00-16:00.hrs.}
    \\
    \href{http://www.swindon-bonsai.co.uk/}{www.swindon-bonsai.co.uk}
    \begin{itemize}
        \item \textbf{\emph{Paul Bowerbank}} \emph{(07982 401103)} \\
        \href{mailto:mailto:paul1561@virginmedia.com}{mailto:paul1561@virginmedia.com} 
    \end{itemize}

    \item \textbf{Friday 21 February 2025 to Sunday 23 February 2025}
    \\
    Trophy Show \\
    Limburghal cv, jaarbeurslaan 6, \\
    B-3600 Genk, Belgium
    \\
    \href{http://www.bonsaiassociation.be/}{www.bonsaiassociation.be}

    \item \textbf{Saturday 8 March 2025 to Sunday 9 March 2025}
    \\
    Dragon Bonsai Spring Show \\
    Open workshop \& Clinic \\
    Aberglasney Gardens, Llangathen, \\
    Carmarthenshire, Wales. SA32 8QH.
    \\
    \emph{£9.50 Children Free} \\
    \emph{Sat 10:00-16:00.hrs Sun 10:00-15:00.hrs}
    \begin{itemize}
        \item \textbf{\emph{Chris Thomas}} \emph{(07798 798194)} \\
        \href{mailto:chris.thomas1@sky.com}{chris.thomas1@sky.com} 
    \end{itemize}

    \item \textbf{Sunday 16 March 2025}
    \\
    Bonsai -Fest \\
    Lady Eastwood Centre, \\
    Newark Showground, \\
    Lincoln Road, Newark, \\
    Nottinghamshire. NG24 2NY. \\
    Demonstrations by: \\
    Graham Potter \\
    Kevin Willson
    \\
    \emph{£10. Accompanied under 16.yrs Free.} \\
    \emph{09:00-16:00.hrs}
    \begin{itemize}
        \item \textbf{\emph{Adam Booty}} \\
        \href{mailto:info@bonsai-fest.com}{info@bonsai-fest.com} 
    \end{itemize}

    \item \textbf{Saturday 22 March 2025 to Sunday 23 March 2025}
    \\
    Sutton Bonsai Society Show \\
    Wisley Gardens, Wisley Lane, \\
    Wisley, Surrey. GU23 6QB
    \\
    \emph{£ tba 10:00-16:30.hrs.}
    \\
    \href{https://www.suttonbonsai.co.uk}{www.suttonbonsai.co.uk}
    \begin{itemize}
        \item \textbf{\emph{Andy Jordan}} \emph{(07958 372101)} \\
        \href{mailto:antique.netsuke@gmail.com}{antique.netsuke@gmail.com} 
    \end{itemize}

    \item \textbf{Sunday 23 March 2025}
    \\
    South East Bonsai Fair \\
    Little Fant Farm, Farleigh Lane, \\
    Maidstone, Kent. ME16 9LY.
    \\
    \emph{Free. 10:00-15:00.hrs}
    \begin{itemize}
        \item \textbf{\emph{Adam Hadley}} \emph{(07765 522117)} \\
        \href{mailto:hadoribonsai@gmail.com}{hadoribonsai@gmail.com} 
    \end{itemize}

    \item \textbf{Sunday 23 March 2025}
    \\
    Friends Of The National Bonsai Collection \\
    Bonsai Boot Sale \\
    Birmingham Botanical Gardens, \\
    Westbourne Road, Edgbaston, \\
    Birmingham. B15 3TR.
    \\
    \emph{FREE. 08:00-12:00.hrs.}
    \begin{itemize}
        \item \textbf{\emph{Kim Turton}} \\
        \href{mailto:turtonkim@hotmail.com}{turtonkim@hotmail.com} 
    \end{itemize}

    \item \textbf{Saturday 29 March 2025}
    \\
    UK Mini Bonsai Group Show \\
    Chobham Village Hall, \\
    Station Road, Chobham, \\
    Surrey. GU24 8AQ. \\
    Supporting Traders: \\
    Daryl Cogavin \\
    Dave Sampson \\
    David Cheshire Bonsai \\
    European Bonsai Pot Collective
    \\
    \emph{£3 cash. 14:00-16:00.hrs}
    \\
    \href{https://www.ukminibonsaigroup.weebly.com}{www.ukminibonsaigroup.weebly.com}
    \begin{itemize}
        \item \textbf{\emph{Gary Careford}} \emph{07478.604599 (Whatsapp Only)} \\
        \href{mailto:ukminibonsaigroup@gmail.com}{ukminibonsaigroup@gmail.com} 
    \end{itemize}

    \item \textbf{Sunday 13 April 2025}
    \\
    6th Expo Bonsai UK \\
    Sponsored by UKBA \\
    K2 Leisure Centre, \\
    Pease Pottage Hill, Crawley, \\
    West Sussex. RH11 9BQ
    \\
    \emph{10:00-15:00.hrs £8 Adults} \\
    \emph{15:00-16:00.hrs £4 Adults} \\
    \emph{Accompanied under 16.yrs Free.}
    \\
    \href{http://www.expobonsaiuk.weebly.co/}{www.expobonsaiuk.weebly.co}
    \begin{itemize}
        \item \textbf{\emph{Steve Hale}} \emph{(07850 771201)} \\
        \href{mailto:ebuk18@gmail.com}{ebuk18@gmail.com} 
    \end{itemize}

    \item \textbf{Sunday 13 April 2025}
    \\
    6th Expo Bonsai UK \\
    Sponsored by UKBA \\
    K2 Leisure Centre, \\
    Pease Pottage Hill, Crawley, \\
    West Sussex. RH11 9BQ
    \\
    \emph{10:00-14:00.hrs £8 Adults} \\
    \emph{15:00-16:00.hrs £4 Adults} \\
    \emph{Accompanied under 16.yrs Free.}
    \\
    \href{http://www.expobonsaiuk.weebly.co/}{www.expobonsaiuk.weebly.co}
    \begin{itemize}
        \item \textbf{\emph{Steve Hale}} \emph{(07850 771201)} \\
        \href{mailto:ebuk18@gmail.com}{ebuk18@gmail.com} 
    \end{itemize}

\end{itemize}
\closearticle