\null
\vfill
\noindent
Copyright \copyright{} 2025 Twickenham Bonsai Club

\null
\noindent
\textit{All rights reserved.}
No part of this book may be reproduced, stored in a retrieval system, or transmitted in any form or by any means, without the prior written permission of the publisher, except in the case of brief quotations embedded in critical articles or reviews.

\noindent
Every effort has been made in the preparation of this book to ensure the accuracy of the information presented.
However, the information contained in this book is sold without warranty, either express or implied.
Neither the editor, nor Twickenham Bonsai Club or its authors and distributors, will be held liable for any damages caused or alleged to have been caused directly or indirectly by this book.

\noindent
Twickenham Bonsai Club has endeavored to provide credits about for all the pictures and content presented in this book.
However, Twickenham Bonsai Club cannot guarantee the accuracy of this information.

\null
\noindent
\textbf{Chairperson:} Tony Ulatowski

\noindent
\textbf{Vice Chairperson:} Tina Todd

\noindent
\textbf{Treasurers:} Brendan Gibbs, Tony Ulatowski

\noindent
\textbf{Secretary:} Nick Lloyd

\noindent
\textbf{Editor:} Stefano Bragaglia \\
\textbf{\textcolor{white}{Editor:}} \textit{With thanks to Jodi Desikan for counting votes and preparing certificates.}\\
\textbf{\textcolor{white}{Editor:}} \textit{Additional contributors credited where appropriate.}

\noindent
\textbf{Proofreaders:} Nick Lloyd, Tina Todd

\noindent
\textbf{Photographers:} Stefano Bragaglia, Steve Palmer, Tina Todd, Tony Ulatowski \\
\textbf{\textcolor{white}{Photographers:}} \textit{Additional contributors credited where appropriate.}

\noindent
\textbf{Multi\--media:} David Fishwick, Haidi Jenkin, Steve Palmer, Tony Ulatowski

\noindent
\textbf{Merchandise:} Brendan Gibbs

\noindent
\textbf{Events:} Laura Shantonas, Tina Todd

\null
\noindent
\textsc{First Edition:} December 2025

\null
\noindent
Published in London by Twickenham Bonsai Club

\null
\begin{center}
    \href{hhttps://www.instagram.com/twickenhambonsaiclub/}{@twickenham\-bonsai\-club}
\end{center}
%\clearpage