\begin{adjustwidth}{1.5cm}{1.5cm}
    \chapter*{Foreword}
    \phantomsection\addcontentsline{toc}{chapter}{Foreword}
    \textit{It gives me great pleasure to introduce this collection of newsletters from the Twickenham Bonsai Club.}
    \textit{Having visited the club many times over the years---right back to its beginnings in Tony's and Nick's gardens---I've had the privilege of watching this community take shape from its very first shoots.}
    \textit{To see how it has grown into such a lively, committed and good\--humoured part of the UK bonsai scene has been genuinely rewarding.}

    \null
    \textit{What has always stood out to me about Twickenham is its attitude.}
    \textit{The quality of the trees continues to improve year after year, but it's the people and the atmosphere that truly define the club.}
    \textit{There is an eagerness to learn, an openness to share knowledge, and a willingness to work together that is far less common than many might think.}
    \textit{That spirit---collaborative, curious, and humble---is exactly what sustains bonsai as an art and as a practice.}

    \null
    \textit{These newsletters capture that feeling remarkably well.}
    \textit{They are not simply records of what happened on a given evening; they represent the collective journey of a club that experiments, asks questions, makes mistakes, celebrates progress, and supports each other along the way.}
    \textit{Bonsai is ultimately transmitted through these interactions far more than through any single demonstration or finished tree.}

    \null
    \textit{I've also been pleased to see the club welcome newcomers so warmly.}
    \textit{A friendly introduction, a bit of encouragement, and the chance to get hands\--on can be what turns a passing interest into a lifelong pursuit.}
    \textit{Twickenham understands this instinctively, and it shows in the steady stream of engaged, enthusiastic members who continue to join.}

    \null
    \textit{Bringing all of this together in one place is a valuable achievement.}
    \textit{I hope this collection not only reflects how far Twickenham Bonsai Club has come, but also serves as a reminder of what can be accomplished when people with a shared passion come together with generosity and purpose.}

    \null
    \textit{The club should be proud of what it has built so far.}
    \textit{If it continues in the same spirit, I have no doubt it will remain a positive and influential presence within the wider UK bonsai community for many years to come.}

    \null
    \hfill \textbf{Peter Warren}

    \hfill Saruyama Bonsai
\end{adjustwidth}
%\cleardoublepage