\begin{adjustwidth}{1.5cm}{1.5cm}
    \chapter*{Preface}
    \phantomsection\addcontentsline{toc}{chapter}{Preface}
    \textit{When I was invited to curate the Twickenham Bonsai Club newsletter last year, I did not expect it to become such a rewarding personal journey.}
    \textit{What began as a simple task of documenting club activity quickly grew into an opportunity to learn, reflect, and better understand both the art of bonsai and the people who practise it.}

    \null
    \textit{As I started to record the club's work, I became increasingly struck by the breadth and quality of what our members were achieving.}
    \textit{Reporting on guest demonstrations, workshops and exhibitions soon became a form of study in itself.}
    \textit{Capturing the careful preparation behind a display, the atmosphere of a successful event, or the quiet satisfaction of members working together helped me realise that bonsai is not only about trees, but about patience, curiosity, craft and community.}
    \textit{In telling these stories, I found myself learning not only technical principles, but also how deeply bonsai touches people's lives.}

    \null
    \textit{The idea of bringing these newsletters together into a single volume emerged naturally from that experience.}
    \textit{This collection is intended as something members can return to over time: to revisit ideas and teachings, to find inspiration in the photographs of past work, and to relive moments of shared effort and camaraderie.}
    \textit{It is, above all, a record of what we have built together in a particular chapter of the club's life.}

    \null
    \textit{In preparing this edition, I have lightly edited the original material.}
    \textit{Obvious spelling errors and typographical mistakes have been corrected where possible, and time\--sensitive sections such as news items and event calendars have been removed to improve clarity and relevance.}
    \textit{Otherwise, the content remains true to its original form and spirit, preserving the character and immediacy of the newsletters as they were first shared.}

    \null
    \textit{This volume would not exist without the generous support of many people.}
    \textit{My sincere thanks go to Tony Ulatowski, Tina Todd and Nick Lloyd for their invaluable help behind the scenes in producing and distributing the newsletter.}
    \textit{I am also grateful to Chris Durne, David Fishwick, the novice members who contributed so thoughtfully to the \textit{Bonsai Roots} section and Jodi Desikan and Steve Palmer for their help with the \textit{Tree of the Month} reports, adding energy and perspective to its pages.}
    \textit{My thanks extend to everyone who tolerated my persistent ideas, answered endless questions, and offered encouragement throughout the year, and to every club member for creating such a welcoming and inclusive community.}

    \null
    \textit{Finally, I would like to thank you, the reader.}
    \textit{Whether you are revisiting familiar memories or discovering these moments for the first time, I hope this collection gives you the same sense of enjoyment, inspiration and belonging that I experienced while putting it together.}

    \null
    \hfill \textbf{Stefano Bragaglia}

    \hfill TWBC Newsletter Editor
\end{adjustwidth}
%\cleardoublepage
