\headline{{\textbf{\Large\sffamily Growing Together:}}\\
          {\textbf{\large\sffamily Bonsai Club News}}}
\label{2025-09-news}
\topic{Save on Club Merchandise with Shared Order!}
\noindent
The club's merchandise can be found at \url{https://overrock.uk/product-category/tw-bonsai/}.
If you're thinking of making a purchase soon, reach out to Brendan on WhatsApp.
Placing a shared order could help save a little on shipping costs.

% \medskip
\topic{Bonsai Resources at Your Fingertips}
\noindent  
Our bonsai club is proud to offer a wide range of resources to help you grow and thrive in your bonsai journey.
All these resources are conveniently organized on our Discord channel.
If you're a subscribed member and haven’t yet accessed the channel, simply \href{https://discord.gg/N6yka6XJ}{follow this link}.

Once you join, you'll land in the \href{https://discord.com/channels/873817545013071872/1118677826208550923}{welcome chat}.
On the left\--hand side, you'll find a list of subchannels, each dedicated to a specific topic or service, such as \href{https://discord.com/channels/873817545013071872/1039691122148130876}{club payments}, \href{https://discord.com/channels/873817545013071872/1001189937409949698}{book recommendations}, and more.

Whether you're a seasoned enthusiast or a new member, these resources are here to support your passion for bonsai.
Don't miss out---get connected today!

% \medskip	
\topic{Bonsai Insights: Information Pack for All Members}
\noindent
We've put together an information pack for all members of the club – from beginners to seasoned enthusiasts.
This pack offers a wealth of resources, including access to a selection of our lockdown ZOOM talks featuring some of the best Bonsai artists in the country.

The following link will direct you to a Google slideshow \href{https://docs.google.com/presentation/d/1L5SRA_ZSvnGMLbRt0CSf-Uz7BaiOfxOs7OUHMM_XrTY/edit?usp=sharing}{New \& Existing Members Information Pack}, so feel free to explore it at your own pace.
We recommend starting with Andy Hardman’s talk on tree biology (Video 1), where he delves into how trees function and what they need to thrive.
\closearticle
\clearpage