\headline{{\textbf{\Large\sffamily Mark Your Calendars:}}\\
{\textbf{\large\sffamily Upcoming Events}}}
\label{2025-02-events}
\noindent
The events listed below refer to club talks, workshops, UK events, and world events registered with the \href{https://www.ukbonsaiassoc.org/events.html}{UK Bonsai Association} as provisional or confirmed, over the next three months.

\begin{itemize}
    \item \textbf{Saturday 8 March 2025 to Sunday 9 March 2025}
    \\
    Dragon Bonsai Spring Show \\
    Open workshop \& Clinic \\
    Aberglasney Gardens, Llangathen, \\
    Carmarthenshire, Wales. SA32 8QH.
    \\
    \emph{£9.50 Children Free} \\
    \emph{Sat 10:00-16:00.hrs Sun 10:00-15:00.hrs}
    \begin{itemize}
        \item \textbf{\emph{Chris Thomas}} \emph{(07798 798194)} \\
        \href{mailto:chris.thomas1@sky.com}{chris.thomas1@sky.com}
    \end{itemize}

    \item \textbf{Sunday 16 March 2025}
    \\
    Bonsai -Fest \\
    Lady Eastwood Centre, \\
    Newark Showground, \\
    Lincoln Road, Newark, \\
    Nottinghamshire. NG24 2NY. \\
    Demonstrations by: \\
    Graham Potter \\
    Kevin Willson
    \\
    \emph{£10. Accompanied under 16.yrs Free.} \\
    \emph{09:00-16:00.hrs}
    \begin{itemize}
        \item \textbf{\emph{Adam Booty}} \\
        \href{mailto:info@bonsai-fest.com}{info@bonsai-fest.com}
    \end{itemize}

    \item \textbf{Saturday 22 March 2025 to Sunday 23 March 2025}
    \\
    Sutton Bonsai Society Show \\
    Wisley Gardens, Wisley Lane, \\
    Wisley, Surrey. GU23 6QB
    \\
    \emph{£ tba 10:00-16:30.hrs.}
    \\
    \href{https://www.suttonbonsai.co.uk}{www.suttonbonsai.co.uk}
    \begin{itemize}
        \item \textbf{\emph{Andy Jordan}} \emph{(07958 372101)} \\
        \href{mailto:antique.netsuke@gmail.com}{antique.netsuke@gmail.com}
    \end{itemize}

    \item \textbf{Sunday 23 March 2025}
    \\
    South East Bonsai Fair \\
    Little Fant Farm, Farleigh Lane, \\
    Maidstone, Kent. ME16 9LY.
    \\
    \emph{Free. 10:00-15:00.hrs}
    \begin{itemize}
        \item \textbf{\emph{Adam Hadley}} \emph{(07765 522117)} \\
        \href{mailto:hadoribonsai@gmail.com}{hadoribonsai@gmail.com}
    \end{itemize}

    \item \textbf{Sunday 23 March 2025}
    \\
    Friends Of The National Bonsai Collection \\
    Bonsai Boot Sale \\
    Birmingham Botanical Gardens, \\
    Westbourne Road, Edgbaston, \\
    Birmingham. B15 3TR.
    \\
    \emph{FREE. 08:00-12:00.hrs.}
    \begin{itemize}
        \item \textbf{\emph{Kim Turton}} \\
        \href{mailto:turtonkim@hotmail.com}{turtonkim@hotmail.com}
    \end{itemize}

    \item \textbf{Saturday 29 March 2025}
    \\
    UK Mini Bonsai Group Show \\
    Chobham Village Hall, \\
    Station Road, Chobham, \\
    Surrey. GU24 8AQ. \\
    07478.604599 (Whatsapp Only) \\
    <u>Supporting Traders:</u> \\
    Daryl Cogavin \\
    Dave Sampson \\
    David Cheshire Bonsai \\
    European Bonsai Pot Collective
    \\
    \emph{£3 cash. 14:00-16:00.hrs}
    \\
    \href{https://www.ukminibonsaigroup.weebly.com}{www.ukminibonsaigroup.weebly.com}
    \begin{itemize}
        \item \textbf{\emph{Gary Careford}} \\
        \href{mailto:ukminibonsaigroup@gmail.com}{ukminibonsaigroup@gmail.com}
    \end{itemize}

    \item \textbf{Sunday 13 April 2025}
    \\
    6th Expo Bonsai UK \\
    Sponsored by UKBA \\
    K2 Leisure Centre, \\
    Pease Pottage Hill, Crawley, \\
    West Sussex. RH11 9BQ
    \\
    \emph{10:00-14:00.hrs £8 Adults} \\
    \emph{15:00-16:00.hrs £4 Adults} \\
    \emph{Accompanied under 16.yrs Free.}
    \\
    \href{http://www.expobonsaiuk.weebly.co/}{www.expobonsaiuk.weebly.co}
    \begin{itemize}
        \item \textbf{\emph{Steve Hale}} \emph{(07850 771201)} \\
        \href{mailto:ebuk18@gmail.com}{ebuk18@gmail.com}
    \end{itemize}

    \item \textbf{Saturday 26 April 2025 to Sunday 27 April 2025}
    \\
    Celtic Bonsai Morten Albek Weekend \\
    Cwmamman Resource Centre, \\
    Station Road, Glanamman, \\
    Ammanford, Carmarthenshire, \\
    Wales. SA18 1LQ.
    \begin{itemize}
        \item \textbf{\emph{Chris Thomas}} \emph{(07798 798194)} \\
        \href{mailto:chris.thomas1@sky.com}{chris.thomas1@sky.com}
    \end{itemize}

    \item \textbf{Saturday 3 May 2025 to Sunday 4 May 2025}
    \\
    The South West Bonsai Show \\
    Sponsored by FoBBS \\
    RHS Rosemoor Gardens, \\
    Torrington, North Devon. EX38 8PH.
    \\
    \emph{tbc. 10:00-18:00.hrs.}
    \\
    \href{https://www.fobbsbonsai.co.uk}{www.fobbsbonsai.co.uk}
    \begin{itemize}
        \item \textbf{\emph{Nigel Wright}} \emph{(07974 998032)} \\
        \href{mailto:coordinator@fobbsbonsai.co.uk}{coordinator@fobbsbonsai.co.uk}
    \end{itemize}

    \item \textbf{Saturday 3 May 2025 to Sunday 4 May 2025}
    \\
    Cornwall Bonsai Society Display \\
    At Trebah Garden Trust, \\
    Mawnan Smith, Nr Falmouth, \\
    Cornwall. TR11 5JZ.
    \\
    \emph{tbc. 09:30-17:00.hrs}
    \\
    \href{https://www.cornwall-bonsai-society.co.uk}{www.cornwall-bonsai-society.co.uk}
    \begin{itemize}
        \item \textbf{\emph{Frank Reid}} \emph{(07588 672268)} \\
        \href{mailto:frank@cornwall-bonsai-society.co.uk}{frank@cornwall-bonsai-society.co.uk}
    \end{itemize}

    \item \textbf{Saturday 3 May 2025 to Sunday 4 May 2025}
    \\
    Accrington \& District Bonsai Society Display \\
    At Barton Grange Garden Centre, \\
    Garstang Road, Brock, \\
    Preston. PR3 0BT.
    \\
    \emph{Free. 09:00-17:30.hrs \& 10:00-16:30.hrs.}
    \\
    \href{https://www.accringtonbonsai.co.uk}{www.accringtonbonsai.co.uk}
    \begin{itemize}
        \item \textbf{\emph{Diane Kennedy}} \emph{(07799 567692)} \\
        \href{mailto:dianestardis@icloud.com}{dianestardis@icloud.com}
    \end{itemize}

    \item \textbf{Saturday 10 May 2025}
    \\
    World Bonsai Day

    \item \textbf{Saturday 10 May 2025 to Sunday 11 May 2025}
    \\
    Greenwood Spring Bonsai Bash \\
    Greenwood Bonsai Studio, \\
    Ollerton Road, Arnold, Nottingham. NG5 8PR.
    \\
    \emph{Free. 10:00-17:00.hrs}
    \\
    \href{https://www.bonsai.co.uk}{www.bonsai.co.uk}
    \begin{itemize}
        \item \textbf{\emph{Corin Tomlinson}} \emph{(01159 205757)} \\
        \href{mailto:office@bonsai.co.uk}{office@bonsai.co.uk}
    \end{itemize}

    \item \textbf{Sunday 11 May 2025}
    \\
    Ayrshire Bonsai Club Open Exhibition \\
    Troon Concert Hall, \\
    South Beach, Troon. \\
    Ayrshire. KA10 6EF.
    \\
    \emph{£2.50. 11:00-16:00.hrs}
    \begin{itemize}
        \item \textbf{\emph{Jeff Banning}} \emph{(07799 477895)} \\
        \href{mailto:jeffbanning@btinternet.com}{jeffbanning@btinternet.com}
    \end{itemize}

    \item \textbf{Friday 16 May 2025 to Sunday 18 May 2025}
    \\
    Southend Bonsai Society Display \\
    At The National Flower Show. \\
    Hylands House, \\
    London Road, Writtle, \\
    Chelmsford, Essex. CM2 8FS.
    \\
    \emph{tba. 09.30-21:00.hrs}
    \begin{itemize}
        \item \textbf{\emph{Paul Schofield}} \emph{(07942 679688)} \\
        \href{mailto:southendbonsaisociety@gmail.com}{southendbonsaisociety@gmail.com}
    \end{itemize}

    \item \textbf{Tuesday 20 May 2025 to Saturday 24 May 2025}
    \\
    FOBBs Bonsai Display \\
    Chelsea Flower Show \\
    Royal Hospital Chelsea, London. SW3 4SR.
    \begin{itemize}
        \item \textbf{\emph{Russell Wheeler}} \emph{(07810 372377)} \\
        \href{mailto:russboy23@gmail.com}{russboy23@gmail.com}
    \end{itemize}

\end{itemize}
\closearticle
\pagebreak
