\headline{{\textbf{\Large\sffamily Mark Your Calendars:}}\\
          {\textbf{\large\sffamily Upcoming Events}}}
\label{2025-03-events}
\noindent
The events listed below refer to club talks, workshops, UK events, and world events registered with the \href{https://www.ukbonsaiassoc.org/events.html}{UK Bonsai Association} as provisional or confirmed, over the next three months.
\begin{itemize}

    \item \textbf{Sunday 16 March 2025}
    \\
    Bonsai -Fest \\
    Lady Eastwood Centre, \\
    Newark Showground, \\
    Lincoln Road, Newark, \\
    Nottinghamshire. NG24 2NY. \\
    Demonstrations by: \\
    Graham Potter \\
    Kevin Willson \\
    Supporting Traders: \\
    Adrian West \\
    Aka Matsu Bonsai School \\
    Akka, Bogwood \\
    Bon-Tag \\
    Bonsai Pots By Ian Jobling \\
    Bonsai Crazy \\
    Bonsai Fellows \\
    Bonsai2u Ltd \\
    Bonsai4me \\
    Brookfield Yamadori \\
    China Mist Bonsai Pottery \\
    Christine \& Stewart Bonsai Pots \\
    Chris Thomas Bonsai \\
    Claire Northcott \\
    Classic Era \\
    Crafty Monkey Shop \\
    Dave Wiseman \\
    David Horwood \\
    David Cheshire Bonsai \\
    David Sampson \\
    Dei Ceramics \\
    Derbyshire Bonsai \\
    Dragonfly Bonsai Pots \\
    Driftwood Bonsai \\
    European Bonsai Potter Collective \\
    Everysprout \\
    Geoff Lloyd \\
    GG Evergreen Bonsai \\
    Glyn \\
    GoBonsai Air \\
    Glynderi Yamadori \\
    Grain Of Time \\
    Green Dragon Bonsai \\
    Greenwood Bonsai Studio \\
    Holden Ceramics \\
    Holland \\
    House Of British Bonsai \& Yamadori \\
    Jill Mitchell \\
    John Farrow \\
    Kenneth Mitchell \\
    Kevin Ward \\
    Majestic Bonsai \\
    Maple Leaf Ceramics \\
    MarPaul Bonsai \\
    Mina San Bonsai \\
    Northern Munki Bonsai \\
    Oliver Wiper \\
    Paul Townsend \\
    Pot Men \\
    Ray Couldwell \\
    Reid Bonsai \\
    RH Bonsai \\
    Rowena Edwards Ceramics \\
    Sam Cousans \\
    Scouse Bonsai \\
    South Yorkshire Bonsai Society \\
    Steve Greaves \\
    Tony Remington Ceramics \\
    Wakai Trees Ltd \\
    Walsall Studio Ceramics \\
    Windybank Bonsai \\
    Zac's Bonsai
    \\
    \emph{£10. Accompanied under 16.yrs Free.} \\
    \emph{09:00-16:00.hrs}
    \begin{itemize}
        \item \textbf{\emph{Adam Booty}} \\
        \href{mailto:info@bonsai-fest.com}{info@bonsai-fest.com} 
    \end{itemize}

    \item \textbf{Sunday 23 March 2025}
    \\
    South East Bonsai Fair \\
    Little Fant Farm, Farleigh Lane, \\
    Maidstone, Kent. ME16 9LY.
    \\
    \emph{Free. 10:00-15:00.hrs}
    \begin{itemize}
        \item \textbf{\emph{Adam Hadley}} \emph{(07765 522117)} \\
        \href{mailto:hadoribonsai@gmail.com}{hadoribonsai@gmail.com} 
    \end{itemize}

    \item \textbf{Sunday 23 March 2025}
    \\
    Friends Of The National Bonsai Collection \\
    Bonsai Boot Sale \\
    Birmingham Botanical Gardens, \\
    Westbourne Road, Edgbaston, \\
    Birmingham. B15 3TR.
    \\
    \emph{FREE. 08:00-12:00.hrs.}
    \begin{itemize}
        \item \textbf{\emph{Kim Turton}} \\
        \href{mailto:turtonkim@hotmail.com}{turtonkim@hotmail.com} 
    \end{itemize}

    \item \textbf{Saturday 29 March 2025}
    \\
    UK Mini Bonsai Group Show \\
    Chobham Village Hall, \\
    Station Road, Chobham, \\
    Surrey. GU24 8AQ. \\
    07478.604599 (Whatsapp Only) \\
    <u>Supporting Traders:</u> \\
    Daryl Cogavin \\
    Dave Sampson \\
    David Cheshire Bonsai \\
    European Bonsai Pot Collective
    \\
    \emph{£3 cash. 14:00-16:00.hrs}
    \\
    \href{https://www.ukminibonsaigroup.weebly.com}{www.ukminibonsaigroup.weebly.com}
    \begin{itemize}
        \item \textbf{\emph{Gary Careford}} \\
        \href{mailto:ukminibonsaigroup@gmail.com}{ukminibonsaigroup@gmail.com} 
    \end{itemize}

    \item \textbf{Sunday 13 April 2025}
    \\
    6th Expo Bonsai UK \\
    Sponsored by UKBA \\
    K2 Leisure Centre, \\
    Pease Pottage Hill, Crawley, \\
    West Sussex. RH11 9BQ
    \\
    \emph{10:00-15:00.hrs £8 Adults} \\
    \emph{15:00-16:00.hrs £4 Adults} \\
    \emph{Accompanied under 16.yrs Free.}
    \\
    \href{http://www.expobonsaiuk.weebly.co/}{www.expobonsaiuk.weebly.co}
    \begin{itemize}
        \item \textbf{\emph{Steve Hale}} \emph{(07850 771201)} \\
        \href{mailto:ebuk18@gmail.com}{ebuk18@gmail.com} 
    \end{itemize}

    \item \textbf{Thursday 24 April 2025 to Sunday 27 April 2025}
    \\
    Yorkshire Bonsai Society Display \& Show \\
    At Harrogate Spring Flower Show, \\
    Great Yorkshire Showground, \\
    Railway Road, Harrogate, \\
    North Yorkshire. HG2 8NZ.
    \\
    \emph{tba. (Exhibitors Free).} \\
    \emph{10:00-17:00.hrs}
    \begin{itemize}
        \item \textbf{\emph{Craig Brown}} \emph{(07763 771701)} \\
        \href{mailto:jcraig008@sky.com}{jcraig008@sky.com} 
    \end{itemize}

    \item \textbf{Saturday 26 April 2025 to Sunday 27 April 2025}
    \\
    Celtic Bonsai Morten Albek Weekend \\
    Cwmamman Resource Centre, \\
    Station Road, Glanamman, \\
    Ammanford, Carmarthenshire, \\
    Wales. SA18 1LQ.
    \begin{itemize}
        \item \textbf{\emph{Chris Thomas}} \emph{(07798 798194)} \\
        \href{mailto:chris.thomas1@sky.com}{chris.thomas1@sky.com} 
    \end{itemize}

    \item \textbf{Saturday 3 May 2025 to Sunday 4 May 2025}
    \\
    The South West Bonsai Show \\
    Sponsored by FoBBS \\
    RHS Rosemoor Gardens, \\
    Torrington, North Devon. EX38 8PH.
    \\
    \emph{tbc. 10:00-18:00.hrs.}
    \\
    \href{https://www.fobbsbonsai.co.uk}{www.fobbsbonsai.co.uk}
    \begin{itemize}
        \item \textbf{\emph{Nigel Wright}} \emph{(07974 998032)} \\
        \href{mailto:coordinator@fobbsbonsai.co.uk}{coordinator@fobbsbonsai.co.uk} 
    \end{itemize}

    \item \textbf{Saturday 3 May 2025 to Sunday 4 May 2025}
    \\
    Cornwall Bonsai Society Display \\
    At Trebah Garden Trust, \\
    Mawnan Smith, Nr Falmouth, \\
    Cornwall. TR11 5JZ.
    \\
    \emph{tbc. 09:30-17:00.hrs}
    \\
    \href{https://www.cornwall-bonsai-society.co.uk}{www.cornwall-bonsai-society.co.uk}
    \begin{itemize}
        \item \textbf{\emph{Frank Reid}} \emph{(07588 672268)} \\
        \href{mailto:frank@cornwall-bonsai-society.co.uk}{frank@cornwall-bonsai-society.co.uk} 
    \end{itemize}

    \item \textbf{Saturday 3 May 2025 to Sunday 4 May 2025}
    \\
    Accrington \& District Bonsai Society Display \\
    At Barton Grange Garden Centre, \\
    Garstang Road, Brock, \\
    Preston. PR3 0BT.
    \\
    \emph{Free. 09:00-17:30.hrs \& 10:00-16:30.hrs.}
    \\
    \href{https://www.accringtonbonsai.co.uk}{www.accringtonbonsai.co.uk}
    \begin{itemize}
        \item \textbf{\emph{Diane Kennedy}} \emph{(07799 567692)} \\
        \href{mailto:dianestardis@icloud.com}{dianestardis@icloud.com} 
    \end{itemize}

    \item \textbf{Sunday 4 May 2025 to Monday 5 May 2025}
    \\
    Manchester Bonsai Society Display \\
    At RHS Bridgewater, \\
    Leigh Road, Worsley, \\
    Salford. M28 2LJ.
    \\
    \emph{tbc. 10:00-16:00.hrs}
    \\
    \href{https://www.manchesterbonsaisociety.uk}{www.manchesterbonsaisociety.uk}
    \begin{itemize}
        \item \textbf{\emph{Wayne Crumpton}} \emph{(07742 111142)} \\
        \href{mailto:mbsmembershipsecretary@gmail.com}{mbsmembershipsecretary@gmail.com} 
    \end{itemize}

    \item \textbf{Saturday 10 May 2025}
    \\
    World Bonsai Day

    \item \textbf{Saturday 10 May 2025 to Sunday 11 May 2025}
    \\
    Greenwood Spring Bonsai Bash \\
    Greenwood Bonsai Studio, \\
    Ollerton Road, Arnold, Nottingham. NG5 8PR.
    \\
    \emph{Free. 10:00-17:00.hrs}
    \\
    \href{https://www.bonsai.co.uk}{www.bonsai.co.uk}
    \begin{itemize}
        \item \textbf{\emph{Corin Tomlinson}} \emph{(01159 205757)} \\
        \href{mailto:office@bonsai.co.uk}{office@bonsai.co.uk} 
    \end{itemize}

    \item \textbf{Sunday 11 May 2025}
    \\
    Ayrshire Bonsai Club Open Exhibition \\
    Troon Concert Hall, \\
    South Beach, Troon. \\
    Ayrshire. KA10 6EF.
    \\
    \emph{£2.50. 11:00-16:00.hrs}
    \begin{itemize}
        \item \textbf{\emph{Jeff Banning}} \emph{(07799 477895)} \\
        \href{mailto:jeffbanning@btinternet.com}{jeffbanning@btinternet.com} 
    \end{itemize}

    \item \textbf{Friday 16 May 2025 to Sunday 18 May 2025}
    \\
    Southend Bonsai Society Display \\
    At The National Flower Show. \\
    Hylands House, \\
    London Road, Writtle, \\
    Chelmsford, Essex. CM2 8FS.
    \\
    \emph{tba. 09.30-21:00.hrs}
    \begin{itemize}
        \item \textbf{\emph{Paul Schofield}} \emph{(07942 679688)} \\
        \href{mailto:southendbonsaisociety@gmail.com}{southendbonsaisociety@gmail.com} 
    \end{itemize}

    \item \textbf{Tuesday 20 May 2025 to Saturday 24 May 2025}
    \\
    FOBBs Bonsai Display \\
    Chelsea Flower Show \\
    Royal Hospital Chelsea, London. SW3 4SR.
    \begin{itemize}
        \item \textbf{\emph{Russell Wheeler}} \emph{(07810 372377)} \\
        \href{mailto:russboy23@gmail.com}{russboy23@gmail.com} 
    \end{itemize}

    \item \textbf{Saturday 24 May 2025}
    \\
    North London Bonsai Group Show \\
    Capel Manor, Bullsmoor Lane, \\
    Enfield, Middlesex. EN1 4RQ. \\
    Supporting Club: \\
    UK Mini Bonsai Group
    \\
    \emph{£10. 10:00-16:00.hrs.}
    \begin{itemize}
        \item \textbf{\emph{Bob McGregor}} \emph{(07903 710509)} \\
        \href{mailto:dismcg@hotmail.co.uk}{dismcg@hotmail.co.uk} 
    \end{itemize}

    \item \textbf{Saturday 24 May 2025 to Monday 26 May 2025}
    \\
    Somerset Bonsai Society Annual Show \\
    Willowbrook Garden Centre, \\
    West Buckland Road, West Buckland, \\
    Nr Wellington, Somerset. TA21 9HX.
    \\
    \emph{Free. 09:00-17:30.hrs.}
    \\
    \href{http://www.somersetbonsaiclub.wordpress.com/}{www.somersetbonsaiclub.wordpress.com}
    \begin{itemize}
        \item \textbf{\emph{Alistair Hodgson}} \emph{(07778 408920)} \\
        \href{mailto:secretary.somersetbonsaiclub@btinternet.com}{secretary.somersetbonsaiclub@btinternet.com} 
    \end{itemize}

    \item \textbf{Monday 26 May 2025}
    \\
    Accrington \& District Bonsai Society Display \\
    At Great Harwood Show, \\
    The New Showground, \\
    Harwood Lane, Great Harwood, \\
    Lancashire. BB6 7UL.
    \\
    \emph{Tba. 09:00-17:00.hrs.}
    \\
    \href{https://www.accringtonbonsai.co.uk}{www.accringtonbonsai.co.uk}
    \begin{itemize}
        \item \textbf{\emph{Diane Kennedy}} \emph{(07799 567692)} \\
        \href{mailto:dianestardis@icloud.com}{dianestardis@icloud.com} 
    \end{itemize}

    \item \textbf{Saturday 31 May 2025}
    \\
    UK Bonsai Association Auction \\
    Chobham Village Hall, \\
    Station Road, Chobham, \\
    Surrey. GU24 8AQ. \\
    The auction is strictly cash only please. \\
    Please visit the auction website for further details \\
    Submissions asap first 200 items only
    \\
    \emph{£2 cash. Children -16 FREE 1100-1600.hrs}
    \\
    \href{https://www.ukbonsaiauction.weebly.com}{www.ukbonsaiauction.weebly.com}
    \begin{itemize}
        \item \textbf{\emph{Mark Moreland}} \emph{(07850 771201)} \\
        \href{mailto:ukbaauction@gmail.com}{ukbaauction@gmail.com} 
    \end{itemize}

    \item \textbf{Sunday 8 June 2025}
    \\
    Bonsai By The Sea. \\
    The Pavilion, The Esplanade, \\
    Exmouth. EX8 2AZ. \\
    Supporting Club: \\
    UK Mini Bonsai Group
    \\
    \emph{£5. 10:00-16:30.hrs.}
    \\
    \href{http://www.exeterbonsaisocety.com/}{www.exeterbonsaisocety.com}
    \begin{itemize}
        \item \textbf{\emph{Brian MacKichan}} \emph{(01392 437525)} \\
        \href{mailto:brian.mackichan@mypostoffice.co.uk}{brian.mackichan@mypostoffice.co.uk} 
    \end{itemize}

    \item \textbf{Sunday 8 June 2025}
    \\
    Midland Bonsai Society Show \\
    Birmingham Botanical Gardens, \\
    Westbourne Road, Edgbaston, \\
    Birmingham. B15 3TR. \\
    Supporting Club: \\
    Redditch Bonsai Society \\
    Supporting Traders: \\
    David Cheshire Bonsai \\
    Funky Fish Ceramics
    \\
    \emph{tba. 10:30-16:00.hrs.}
    \\
    \href{https://www.midlandbonsai.org}{www.midlandbonsai.org}
    \begin{itemize}
        \item \textbf{\emph{Richard Gilkes}} \emph{(07803 593024)} \\
        \href{mailto:ragilkes@blueyonder.co.uk}{ragilkes@blueyonder.co.uk} 
    \end{itemize}

    \item \textbf{Saturday 14 June 2025}
    \\
    Accrington \& District Bonsai Society Display \\
    At Nursery End Garden Centre, \\
    Harrington Street, Clayton Le Moors, \\
    Accrington. BB5 4DF.
    \\
    \emph{Free. 09:30-17:00.hrs.}
    \\
    \href{https://www.accringtonbonsai.co.uk}{www.accringtonbonsai.co.uk}
    \begin{itemize}
        \item \textbf{\emph{Diane Kennedy}} \emph{(07799 567692)} \\
        \href{mailto:dianestardis@icloud.com}{dianestardis@icloud.com} 
    \end{itemize}

    \item \textbf{Saturday 14 June 2025 to Sunday 15 June 2025}
    \\
    Mid-Herts Bonsai Society \\
    Kingsbury Barn, Branch Road, \\
    St Albans, Hertfordshire. AL3 4SE.
    \\
    \emph{Free. 11:00-17:00.hrs}
    \\
    \href{https://www.midhertsbonsaiclub.co.uk}{www.midhertsbonsaiclub.co.uk}
    \begin{itemize}
        \item \textbf{\emph{Geoff Conybeare}} \emph{(07396 732817)} \\
        \href{mailto:info@midhertsbonsaiclub.co.uk}{info@midhertsbonsaiclub.co.uk} 
    \end{itemize}

\end{itemize}
\closearticle