\headline{{\textbf{\Large\sffamily Mark Your Calendars:}}\\
          {\textbf{\large\sffamily Upcoming Events}}}
\label{2025-05-events}

The events listed below refer to club talks, workshops, UK events, and world events registered with the \href{https://www.ukbonsaiassoc.org/events.html}{UK Bonsai Association} as provisional or confirmed, over the next three months.
\begin{itemize}

    \item \textbf{Saturday 3 May 2025 to Sunday 4 May 2025}
    \\
    The South West Bonsai Show \\
    Sponsored by FoBBS \\
    RHS Rosemoor Gardens, \\
    Torrington, North Devon. EX38 8PH. \\
    Supporting Clubs: \\
    Bristol Bonsai Society \\
    Cardiff Bonsai Society \\
    Dragon Bonsai Club \\
    Exeter Bonsai Society \\
    North Devon Bonsai Society \\
    Plymouth Bonsai Society \\
    Somerset Bonsai Society \\
    South Devon Bonsai Society \\
    Supporting Traders: \\
    Brian MacKichan Bonsai \\
    David Cheshire Bonsai \\
    Mendip Bonsai Studio \\
    The Consortium \\
    Thyme and Space \\
    Wood and Clay
    \\
    \emph{tbc. 10:00-18:00.hrs.}
    \\
    \href{https://www.fobbsbonsai.co.uk}{www.fobbsbonsai.co.uk}
    \begin{itemize}
        \item \textbf{\emph{Nigel Wright}} \emph{(07974 998032)} \\
        \href{mailto:coordinator@fobbsbonsai.co.uk}{coordinator@fobbsbonsai.co.uk} 
    \end{itemize}

    \item \textbf{Saturday 3 May 2025 to Sunday 4 May 2025}
    \\
    Cornwall Bonsai Society Display \\
    At Trebah Garden Trust, \\
    Mawnan Smith, Nr Falmouth, \\
    Cornwall. TR11 5JZ.
    \\
    \emph{tbc. 09:30-17:00.hrs}
    \\
    \href{https://www.cornwall-bonsai-society.co.uk}{www.cornwall-bonsai-society.co.uk}
    \begin{itemize}
        \item \textbf{\emph{Frank Reid}} \emph{(07588 672268)} \\
        \href{mailto:frank@cornwall-bonsai-society.co.uk}{frank@cornwall-bonsai-society.co.uk} 
    \end{itemize}

    \item \textbf{Saturday 3 May 2025 to Sunday 4 May 2025}
    \\
    Accrington \& District Bonsai Society Display \\
    At Barton Grange Garden Centre, \\
    Garstang Road, Brock, \\
    Preston. PR3 0BT.
    \\
    \emph{Free. 09:00-17:30.hrs \& 10:00-16:30.hrs.}
    \\
    \href{https://www.accringtonbonsai.co.uk}{www.accringtonbonsai.co.uk}
    \begin{itemize}
        \item \textbf{\emph{Diane Kennedy}} \emph{(07799 567692)} \\
        \href{mailto:dianestardis@icloud.com}{dianestardis@icloud.com} 
    \end{itemize}

    \item \textbf{Sunday 4 May 2025 to Monday 5 May 2025}
    \\
    Manchester Bonsai Society Display \\
    At RHS Bridgewater, \\
    Leigh Road, Worsley, \\
    Salford. M28 2LJ.
    \\
    \emph{tbc. 10:00-16:00.hrs}
    \\
    \href{https://www.manchesterbonsaisociety.uk}{www.manchesterbonsaisociety.uk}
    \begin{itemize}
        \item \textbf{\emph{Wayne Crumpton}} \emph{(07742 111142)} \\
        \href{mailto:mbsmembershipsecretary@gmail.com}{mbsmembershipsecretary@gmail.com} 
    \end{itemize}

    \item \textbf{Saturday 10 May 2025}
    \\
    World Bonsai Day

    \item \textbf{Saturday 10 May 2025 to Sunday 11 May 2025}
    \\
    Greenwood Spring Bonsai Bash \\
    Greenwood Bonsai Studio, \\
    Ollerton Road, Arnold, Nottingham. NG5 8PR.
    \\
    \emph{Free. 10:00-17:00.hrs}
    \\
    \href{https://www.bonsai.co.uk}{www.bonsai.co.uk}
    \begin{itemize}
        \item \textbf{\emph{Corin Tomlinson}} \emph{(01159 205757)} \\
        \href{mailto:office@bonsai.co.uk}{office@bonsai.co.uk} 
    \end{itemize}

    \item \textbf{Sunday 11 May 2025}
    \\
    Ayrshire Bonsai Club Open Exhibition \\
    Troon Concert Hall, \\
    South Beach, Troon. \\
    Ayrshire. KA10 6EF.
    \\
    \emph{£2.50. 11:00-16:00.hrs}
    \begin{itemize}
        \item \textbf{\emph{Jeff Banning}} \emph{(07799 477895)} \\
        \href{mailto:jeffbanning@btinternet.com}{jeffbanning@btinternet.com} 
    \end{itemize}

    \item \textbf{Friday 16 May 2025 to Sunday 18 May 2025}
    \\
    Southend Bonsai Society Display \\
    At The National Flower Show. \\
    Hylands House, \\
    London Road, Writtle, \\
    Chelmsford, Essex. CM2 8FS.
    \\
    \emph{tba. 09.30-21:00.hrs}
    \begin{itemize}
        \item \textbf{\emph{Paul Schofield}} \emph{(07942 679688)} \\
        \href{mailto:southendbonsaisociety@gmail.com}{southendbonsaisociety@gmail.com} 
    \end{itemize}

    \item \textbf{Tuesday 20 May 2025 to Saturday 24 May 2025}
    \\
    FOBBs Bonsai Display \\
    Chelsea Flower Show \\
    Royal Hospital Chelsea, London. SW3 4SR.
    \begin{itemize}
        \item \textbf{\emph{Russell Wheeler}} \emph{(07810 372377)} \\
        \href{mailto:russboy23@gmail.com}{russboy23@gmail.com} 
    \end{itemize}

    \item \textbf{Saturday 24 May 2025}
    \\
    North London Bonsai Group Show \\
    Capel Manor, Bullsmoor Lane, \\
    Enfield, Middlesex. EN1 4RQ. \\
    Supporting Club: \\
    UK Mini Bonsai Group
    \\
    \emph{£10. 10:00-16:00.hrs.}
    \begin{itemize}
        \item \textbf{\emph{Bob McGregor}} \emph{(07903 710509)} \\
        \href{mailto:dismcg@hotmail.co.uk}{dismcg@hotmail.co.uk} 
    \end{itemize}

    \item \textbf{Saturday 24 May 2025 to Monday 26 May 2025}
    \\
    Somerset Bonsai Society Annual Show \\
    Willowbrook Garden Centre, \\
    West Buckland Road, West Buckland, \\
    Nr Wellington, Somerset. TA21 9HX.
    \\
    \emph{Free. 09:00-17:30.hrs.}
    \\
    \href{http://www.somersetbonsaiclub.wordpress.com/}{www.somersetbonsaiclub.wordpress.com}
    \begin{itemize}
        \item \textbf{\emph{Alistair Hodgson}} \emph{(07778 408920)} \\
        \href{mailto:secretary.somersetbonsaiclub@btinternet.com}{secretary.somersetbonsaiclub@btinternet.com} 
    \end{itemize}

    \item \textbf{Sunday 25 May 2025}
    \\
    Kent Bonsai Society Show \\
    Dunkirk Village Hall, London Road, \\
    Dunkirk, Kent. ME13 9LG.
    \\
    \emph{£3. 1000-1600.hrs}
    \\
    \href{http://kentbonsaiclub.weebly.com/}{kentbonsaiclub.weebly.com}
    \begin{itemize}
        \item \textbf{\emph{George Long}} \emph{(01227 768841 07850974410)} \\
        \href{mailto:longdax@btinternet.com}{longdax@btinternet.com} 
    \end{itemize}

    \item \textbf{Monday 26 May 2025}
    \\
    Accrington \& District Bonsai Society Display \\
    At Great Harwood Show, \\
    The New Showground, \\
    Harwood Lane, Great Harwood, \\
    Lancashire. BB6 7UL.
    \\
    \emph{Tba. 09:00-17:00.hrs.}
    \\
    \href{https://www.accringtonbonsai.co.uk}{www.accringtonbonsai.co.uk}
    \begin{itemize}
        \item \textbf{\emph{Diane Kennedy}} \emph{(07799 567692)} \\
        \href{mailto:dianestardis@icloud.com}{dianestardis@icloud.com} 
    \end{itemize}

    \item \textbf{Sunday 1 June 2025}
    \\
    UK Bonsai Association Auction \\
    Chobham Village Hall, \\
    Station Road, Chobham, \\
    Surrey. GU24 8AQ. \\
    The auction is strictly cash only please. \\
    Please visit the auction website for further details \\
    Submissions asap first 200 items only
    \\
    \emph{£2 cash. Children -16 FREE 1100-1600.hrs}
    \\
    \href{https://www.ukbonsaiauction.weebly.com}{www.ukbonsaiauction.weebly.com}
    \begin{itemize}
        \item \textbf{\emph{Mark Moreland}} \emph{(07850 771201)} \\
        \href{mailto:ukbaauction@gmail.com}{ukbaauction@gmail.com} 
    \end{itemize}

    \item \textbf{Sunday 8 June 2025}
    \\
    Bonsai By The Sea. \\
    The Pavilion, The Esplanade, \\
    Exmouth. EX8 2AZ. \\
    <u>Supporting Clubs:</u> \\
    British Suiseki Club \\
    Cardiff Bonsai Society \\
    Celtic Knot Bonsai Society \\
    Cornwall Bonsai Society \\
    Dragon Bonsai Society \\
    Exeter Bonsai Society \\
    North Devon Bonsai Society \\
    Plymouth Bonsai Society \\
    South Devon Bonsai Society \\
    UK Mini Bonsai Group \\
    <u>Supporting Traders:</u> \\
    Chris Thomas Bonsai \\
    Devon Bonsai \\
    Kevin Jenkins Pottery \\
    Kevin Strong Bonsai \\
    Observatory Bonsai \\
    Wood and Clay Ceramics
    \\
    \emph{£5. 10:00-16:30.hrs.}
    \\
    \href{http://www.exeterbonsaisocety.com/}{www.exeterbonsaisocety.com}
    \begin{itemize}
        \item \textbf{\emph{Brian MacKichan}} \emph{(01392 437525)} \\
        \href{mailto:brian.mackichan@mypostoffice.co.uk}{brian.mackichan@mypostoffice.co.uk} 
    \end{itemize}

    \item \textbf{Sunday 8 June 2025}
    \\
    Midland Bonsai Society Show \\
    Birmingham Botanical Gardens, \\
    Westbourne Road, Edgbaston, \\
    Birmingham. B15 3TR. \\
    Supporting Club: \\
    Redditch Bonsai Society \\
    Supporting Traders: \\
    David Cheshire Bonsai \\
    Funky Fish Ceramics
    \\
    \emph{tba. 10:30-16:00.hrs.}
    \\
    \href{https://www.midlandbonsai.org}{www.midlandbonsai.org}
    \begin{itemize}
        \item \textbf{\emph{Richard Gilkes}} \emph{(07803 593024)} \\
        \href{mailto:ragilkes@blueyonder.co.uk}{ragilkes@blueyonder.co.uk} 
    \end{itemize}

    \item \textbf{Sunday 8 June 2025}
    \\
    North East Lincolnshire \& Humberside \\
    Bonsai Show \\
    Darby \& Joan Hall, \\
    58 Finkle Street, Cottingham. HU16 4AZ.
    \\
    \emph{£1.50 -16s Free. 10:00-15:00.hrs}
    \\
    \href{http://www.nelincsbonsai.org.uk/}{www.nelincsbonsai.org.uk}
    \begin{itemize}
        \item \textbf{\emph{Ian Butland}} \emph{(07963 470696)} \\
        \href{mailto:nelbs.chairman@virginmedia.com}{nelbs.chairman@virginmedia.com} 
    \end{itemize}

    \item \textbf{Thursday 12 June 2025 to Sunday 15 June 2025}
    \\
    South Staffs Bonsai Society Display \\
    At Gardeners World Live \\
    National Exhibition Centre \\
    North Avenue, Marston Green, \\
    Birmingham. B40 1NT.
    \begin{itemize}
        \item \textbf{\emph{Dave Barnsley}} \emph{(01216 822200)} \\
        \href{mailto:davidbarnsley@blueyonder.co.uk}{davidbarnsley@blueyonder.co.uk} 
    \end{itemize}

    \item \textbf{Saturday 14 June 2025}
    \\
    Accrington \& District Bonsai Society Display \\
    At Nursery End Garden Centre, \\
    Harrington Street, Clayton Le Moors, \\
    Accrington. BB5 4DF.
    \\
    \emph{Free. 09:30-17:00.hrs.}
    \\
    \href{https://www.accringtonbonsai.co.uk}{www.accringtonbonsai.co.uk}
    \begin{itemize}
        \item \textbf{\emph{Diane Kennedy}} \emph{(07799 567692)} \\
        \href{mailto:dianestardis@icloud.com}{dianestardis@icloud.com} 
    \end{itemize}

    \item \textbf{Saturday 14 June 2025 to Sunday 15 June 2025}
    \\
    Mid-Herts Bonsai Society \\
    Kingsbury Barn, Branch Road, \\
    St Albans, Hertfordshire. AL3 4SE.
    \\
    \emph{Free. 11:00-17:00.hrs}
    \\
    \href{https://www.midhertsbonsaiclub.co.uk}{www.midhertsbonsaiclub.co.uk}
    \begin{itemize}
        \item \textbf{\emph{Geoff Conybeare}} \emph{(07396 732817)} \\
        \href{mailto:info@midhertsbonsaiclub.co.uk}{info@midhertsbonsaiclub.co.uk} 
    \end{itemize}

    \item \textbf{Sunday 15 June 2025}
    \\
    Bristol Bonsai Society Show \\
    Failand Village Hall, Oxhouse Lane, \\
    Failand, Somerset. BS8 3TS.
    \\
    \emph{£6. Under 16s Free.} \\
    \emph{10:00-16:00.hrs}
    \\
    \href{http://www.bristolbonsaisociety.com/}{www.bristolbonsaisociety.com}
    \begin{itemize}
        \item \textbf{\emph{Mark Wood}} \emph{(07964 249279)} \\
        \href{mailto:bbs-site@outlook.com}{bbs-site@outlook.com} 
    \end{itemize}

    \item \textbf{Sunday 15 June 2025}
    \\
    Bedfordshire Bonsai Society Show \\
    Stockwood Park Discovery Centre, \\
    London Road, Luton, \\
    Bedfordshire. LU1 4LX.
    \\
    \emph{Free. 11:00-16:30.hrs}
    \\
    \href{https://www.bedfordshirebonsaisociety.weebly.com}{www.bedfordshirebonsaisociety.weebly.com}
    \begin{itemize}
        \item \textbf{\emph{Richard Gaiger}} \emph{(07745 507318)} \\
        \href{mailto:r.gaiger@ntlworld.com}{r.gaiger@ntlworld.com} 
    \end{itemize}

    \item \textbf{Sunday 15 June 2025}
    \\
    Chiltern Bonsai Society Show \\
    Liston Hall, Chapel Street, Marlow, \\
    Buckinghamshire, SL7 1DD \\
    Supporting Clubs: \\
    Middlesex Bonsai Society \\
    UK Mini Bonsai Group
    \\
    \emph{£2 -16s Free. 10:00-16:00.hrs.}
    \\
    \href{https://www.chilternbonsai.org.uk}{www.chilternbonsai.org.uk}
    \begin{itemize}
        \item \textbf{\emph{Michael Pegg}} \\
        \href{mailto:mikew.pegg@btinternet.com}{mikew.pegg@btinternet.com} 
        \item \textbf{\emph{Adrian Garnett}} \\
        \href{mailto:adrian.garnett@virginmedia.com}{adrian.garnett@virginmedia.com} 
    \end{itemize}

    \item \textbf{Saturday 21 June 2025}
    \\
    Middlesex Bonsai Society Summer Show \\
    South Harrow Methodist Church, \\
    Walton Avenue, South Harrow, \\
    Middlesex. HA2 8QU.
    \\
    \emph{Free. 10:00-13:00.hrs.}
    \\
    \href{https://middlesexbonsaisociety.weebly.com/}{middlesexbonsaisociety.weebly.com}
    \begin{itemize}
        \item \textbf{\emph{Mark Moreland}} \emph{(07850 771201)} \\
        \href{mailto:markmoreland@live.co.uk}{markmoreland@live.co.uk} 
    \end{itemize}

    \item \textbf{Saturday 21 June 2025}
    \\
    Manchester Bonsai Society Annual Show \\
    At Lymm United Reformed Church, \\
    Brookside Road, Lymm, \\
    Cheshire. WA13 0WQ.
    \\
    \emph{Free. 10:00-16:00.hrs}
    \\
    \href{https://www.manchesterbonsaisociety.uk}{www.manchesterbonsaisociety.uk}
    \begin{itemize}
        \item \textbf{\emph{Wayne Crumpton}} \emph{(07742 111142)} \\
        \href{mailto:mbsmembershipsecretary@gmail.com}{mbsmembershipsecretary@gmail.com} 
    \end{itemize}

    \item \textbf{Sunday 22 June 2025}
    \\
    Blackmore Vale Bonsai Group Show \\
    Charlton Remembrance Hall, \\
    Charlton, Shaftsbury, Dorset. SP7 0PL.
    \\
    \emph{£4.00 Under 16s Free.} \\
    \emph{11:00-15:00.hrs}
    \\
    \href{https://www.blackmorevalebonsaigroup.com}{www.blackmorevalebonsaigroup.com}
    \begin{itemize}
        \item \textbf{\emph{Geoff}} \emph{(07837 781744)} \\
        \href{mailto:m5eay.geoff@btinternet.com}{m5eay.geoff@btinternet.com} 
    \end{itemize}

    \item \textbf{Sunday 22 June 2025}
    \\
    Southend Bonsai Society Spring Show \\
    Ashingdon Memorial Hall, \\
    Ashingdon Road, Rochford, \\
    Essex. SS4 3HF.
    \\
    \emph{£4. 10:00-16:00.hrs}
    \begin{itemize}
        \item \textbf{\emph{Paul Schofield}} \emph{(07942 679688)} \\
        \href{mailto:southendbonsaisociety@gmail.com}{southendbonsaisociety@gmail.com} 
    \end{itemize}

    \item \textbf{Sunday 29 June 2025}
    \\
    Twickenham Bonsai Club Summer Show \\
    St Richard Reynolds Catholic College, \\
    Clifden Road, Twickenham. TW1 4LT.
    \\
    \emph{10:00-14:00.hrs £5 Adults} \\
    \emph{14:00-16:00.hrs £2.50 Adults} \\
    \emph{Accompanied under 16.yrs Free.}
    \\
    \href{https://www.twbclub.uk}{www.twbclub.uk}
    \begin{itemize}
        \item \textbf{\emph{Tina Todd}} \emph{(07801 582553)} \\
        \href{mailto:toddytl@hotmail.co.uk}{toddytl@hotmail.co.uk} 
    \end{itemize}

    \item \textbf{Sunday 29 June 2025}
    \\
    Penkridge Bonsai Fair \\
    Penkridge Markets, \\
    Clovelly, Pinfold Lane, \\
    Penkridge, Staffordshire. ST19 5AP.
    \\
    \emph{Free. 09:00-14:00.hrs}
    \begin{itemize}
        \item \textbf{\emph{Mark Akins}} \\
        \href{mailto:penkridge@beechfieldbonsai.co.uk}{penkridge@beechfieldbonsai.co.uk} 
    \end{itemize}

    \item \textbf{Tuesday 1 July 2025 to Sunday 6 July 2025}
    \\
    UKBA Bonsai Display \\
    Hampton Court Palace Garden Festival \\
    East Molesley, Surrey. KT8 9AU.
    \begin{itemize}
        \item \textbf{\emph{Russell Wheeler}} \emph{(07810 372377)} \\
        \href{mailto:russboy23@gmail.com}{russboy23@gmail.com} 
    \end{itemize}

    \item \textbf{Sunday 13 July 2025}
    \\
    Surrey Heath Bonsai Show \\
    Chobham Village Hall, \\
    Station Road, Chobham, \\
    Surrey. GU24 8AQ. \\
    Supporting Club: \\
    UK Mini Bonsai Group
    \\
    \emph{Free. 10:00-16:00.hrs.}
    \\
    \href{https://www.surreyheathbonsai.org.uk}{www.surreyheathbonsai.org.uk}
    \begin{itemize}
        \item \textbf{\emph{Chris Rhodes}} \emph{(01276 20893)} \\
        \href{mailto:rhodes163@googlemail.com}{rhodes163@googlemail.com} 
    \end{itemize}

    \item \textbf{Friday 18 July 2025 to Sunday 20 July 2025}
    \\
    Accrington \& District Bonsai Society Display \\
    At Royal Lancashire Show, \\
    Salesbury Hall, Salesbury Hall Road, \\
    Ribchester, Lancashire. PR3 3XR.
    \\
    \emph{tba. 09:30-17:00.hrs.}
    \\
    \href{https://www.accringtonbonsai.co.uk}{www.accringtonbonsai.co.uk}
    \begin{itemize}
        \item \textbf{\emph{Diane Kennedy}} \emph{(07799 567692)} \\
        \href{mailto:dianestardis@icloud.com}{dianestardis@icloud.com} 
    \end{itemize}

    \item \textbf{Saturday 19 July 2025}
    \\
    Surrey Heath Bonsai Society Display \\
    At Wood Street Village Show, \\
    Village Green, Wood Street, \\
    Guildford, Surrey. GU3 3EU
    \\
    \emph{Free. 12:00-17:00.hrs.}
    \\
    \href{https://www.surreyheathbonsai.org.uk}{www.surreyheathbonsai.org.uk}
    \begin{itemize}
        \item \textbf{\emph{Chris Rhodes}} \emph{(01276 20893)} \\
        \href{mailto:rhodes163@googlemail.com}{rhodes163@googlemail.com} 
    \end{itemize}

    \item \textbf{Saturday 19 July 2025 to Sunday 20 July 2025}
    \\
    Chichester Bonsai Exhibition \\
    Manor Nursery, Pagham Road, \\
    Runcton, Chichester. PO20 1LJ. \\
    Supporting Trader: \\
    Collette's Bonsai
    \\
    \emph{Free. 10:00-16:00 \& 10:00-15:00.hrs.}
    \\
    \href{http://www.chichesterbonsai.uk/}{www.chichesterbonsai.uk}
    \begin{itemize}
        \item \textbf{\emph{Liz Panton}} \emph{(07368 327244)} \\
        \href{mailto:lizpanton5@gmail.com}{lizpanton5@gmail.com} 
    \end{itemize}

    \item \textbf{Sunday 20 July 2025}
    \\
    Akamatsu School Of Bonsai Club Show \\
    Azure Garden Centre, \\
    Station Road, Cramlington, \\
    Northumberland. NE23 8BJ.
    \\
    \emph{Free. 1000-1600.hrs}
    \begin{itemize}
        \item \textbf{\emph{Graham Walker}} \emph{(01287 637734)} \\
        \href{mailto:graham.walker11@ntlworld.com}{graham.walker11@ntlworld.com} 
    \end{itemize}

\end{itemize}
\closearticle