\begin{adjustwidth}{1.5cm}{1.5cm}
    \chapter*{Foreword}
    \phantomsection\addcontentsline{toc}{chapter}{Foreword}
    \textit{It gives me great pleasure to introduce this collection of newsletters from the Twickenham Bonsai Club.}
    \textit{In a relatively short space of time, the club has grown into a vibrant, welcoming and highly active part of the UK bonsai community, and it has been genuinely impressive to watch that journey unfold.}

    \null
    \textit{What stands out most about Twickenham is not only the quality of the trees they grow and style, but the spirit behind the club.}
    \textit{There is a real sense of enthusiasm, generosity and teamwork that runs through everything they do.}
    \textit{From hosting respected guest demonstrators and running well\--attended workshops, to supporting shows and encouraging members to develop solid, thoughtful horticultural practice, the club has embraced its role as a centre for learning and sharing.}
    \textit{That is exactly what keeps our art alive and moving forward.}

    \null
    \textit{These newsletters capture that ethos beautifully.}
    \textit{They are far more than simple records of meetings and events; they are a living account of curiosity, experimentation, craftsmanship and community.}
    \textit{They show how bonsai is passed on --- not just through finished trees, but through conversation, patience, shared mistakes and shared successes.}
    \textit{I am especially pleased to see how much effort the club puts into engaging newcomers, as it's often that first warm welcome that turns an interest into a lifelong passion.}

    \null
    \textit{It is encouraging to see all of this gathered in one place.}
    \textit{I hope this collection serves not only as a record of progress for Twickenham, but also as inspiration for other clubs to continue raising their own standards, building connections and nurturing the next generation of bonsai enthusiasts.}

    \null
    \textit{Twickenham Bonsai Club should be proud of what it has achieved so far.}
    \textit{If it continues in this spirit, I have no doubt it will remain an important and positive force within the wider UK bonsai community for many years to come.}

    \null
    \hfill --- \textbf{Mark Moreland}

    \hfill Head, UK Bonsai Association
\end{adjustwidth}
%\cleardoublepage