\headline{{\textbf{\Large\sffamily Mark Your Calendars:}}\\
          {\textbf{\large\sffamily Upcoming Events}}}
\label{2025-12-events}

The events listed below refer to club talks, workshops, UK events, and world events registered with the \href{https://www.ukbonsaiassoc.org/events.html}{UK Bonsai Association} as provisional or confirmed, over the next three months.
\begin{itemize}

    \item \textbf{Sunday 11 January 2026}
    \\
    Ayrshire Bonsai Club Winter Image Show \\
    Alloway Village Hall, 36a Alloway, \\
    Ayrshire. KA7 4PY.
    \\
    \emph{Free. 13:30-17:00.}
    \begin{itemize}
        \item \textbf{\emph{Jeff Banning}} \emph{(07799 477895)} \\
        \href{mailto:jeffbanning@btinternet.com}{jeffbanning@btinternet.com} 
    \end{itemize}

    \item \textbf{Saturday 17 January 2026}
    \\
    Middlesex Bonsai Society Winter Show \\
    South Harrow Methodist Church, \\
    Walton Avenue, South Harrow, \\
    Middlesex. HA2 8QU.
    \\
    \emph{Free. 10:00-13:00.}
    \\
    \href{https://www.middlesexbonsaisociety.weebly.com}{www.middlesexbonsaisociety.weebly.com}
    \begin{itemize}
        \item \textbf{\emph{Darshan Patel}} \emph{(07803 423701)} \\
        \href{mailto:darshanspatel@hotmail.com}{darshanspatel@hotmail.com} 
    \end{itemize}

    \item \textbf{Sunday 1 February 2026}
    \\
    Twickenham Bonsai Club Winter Show \\
    St Richard Reynolds Catholic College, \\
    Clifden Road, Twickenham. TW1 4LT.
    \\
    \emph{10:00-14:00. £5 Adults.} \\
    \emph{14:00-16:00. £2.50 Adults.} \\
    \emph{Accompanied under 16.yrs Free.}
    \\
    \href{https://www.twbclub.uk}{www.twbclub.uk}
    \begin{itemize}
        \item \textbf{\emph{Tina Todd}} \emph{(07801 582553)} \\
        \href{mailto:toddytl@hotmail.co.uk}{toddytl@hotmail.co.uk} 
    \end{itemize}

    \item \textbf{Saturday 7 February 2026 to Sunday 8 February 2026}
    \\
    Irish National Bonsai Exhibition \\
    The People's Museum, \\
    Pery Square, Limerick, \\
    Ireland. V94 HF53.
    \\
    \emph{tba. 10:00-17:00.}
    \begin{itemize}
        \item \textbf{\emph{Philip Donnelly}} \emph{(07990 756988)} \\
        \href{mailto:irishbonsaiexhibition@gmail.com}{irishbonsaiexhibition@gmail.com} 
    \end{itemize}

    \item \textbf{Sunday 15 February 2026}
    \\
    Swindon Bonsai Society Winter Image Show \\
    Grange Leisure Centre, Grange Drive, \\
    Stratton St Margaret, Swindon, \\
    Wiltshire. SN3 4JY. \\
    Supporting Clubs: \\
    Ashfield Bonsai Society \\
    Bristol Bonsai Society \\
    Eastleigh Bonsai Society \\
    Glynderi Bonsai Society \\
    Newbury Bonsai Society \\
    Splinter Group \\
    Surrey Heath Bonsai Society \\
    Twickenham Bonsai Society \\
    Warminster Bonsai Society \\
    Supporting Traders: \\
    China Mist Ceramics \\
    Chris Thomas Bonsai \\
    Dan Barton Ceramics \\
    Dan Butler Ceramics \\
    Dragon Fly Ceramics \\
    Gordon Duffett Ceramics \\
    Green Dragon \\
    Greenwood Bonsai \\
    Lee Verhorevoort Bonsai \\
    Mendip Bonsai \\
    Suteki \\
    Tony Remington Ceramics \\
    Walsall Studio Ceramics \\
    Windybank Bonsai \\
    Zac's Bonsai
    \\
    \emph{£7 -16.yrs Free. 10:00-16:00.}
    \\
    \href{http://www.swindon-bonsai.co.uk/}{www.swindon-bonsai.co.uk}
    \begin{itemize}
        \item \textbf{\emph{Paul Bowerbank}} \emph{(07982 401103)} \\
        \href{mailto:mailto:paul1561@virginmedia.com}{mailto:paul1561@virginmedia.com} 
    \end{itemize}

    \item \textbf{Sunday 8 March 2026}
    \\
    Penkridge Bonsai Fair \\
    Penkridge Markets, \\
    Clovelly, Pinfold Lane, \\
    Penkridge, Staffordshire. ST19 5AP.
    \\
    \emph{Free. 09:00-16:00.}
    \begin{itemize}
        \item \textbf{\emph{Mark Akins}} \\
        \href{mailto:penkridge@beechfieldbonsai.co.uk}{penkridge@beechfieldbonsai.co.uk} 
    \end{itemize}

    \item \textbf{Sunday 22 March 2026}
    \\
    South East Bonsai Fair \\
    Little Fant Farm, Farleigh Lane, \\
    Maidstone, Kent. ME16 9LY.
    \\
    \emph{Free. 10:00-15:00.}
    \begin{itemize}
        \item \textbf{\emph{Adam Hadley}} \emph{(07765 522117)} \\
        \href{mailto:hadoribonsai@gmail.com}{hadoribonsai@gmail.com} 
    \end{itemize}

    \item \textbf{Sunday 22 March 2026}
    \\
    Bonsai -Fest \\
    George Stephenson Hall, \\
    Newark Showground, \\
    Lincoln Road, Newark, \\
    Nottinghamshire. NG24 2NY.
    \\
    \emph{£12.50. -16s Free. 09:00-16:00.}
    \begin{itemize}
        \item \textbf{\emph{Adam Booty}} \\
        \href{mailto:info@bonsai-fest.com}{info@bonsai-fest.com} 
    \end{itemize}

\end{itemize}
\closearticle